

% \documentclass[12pt]{extarticle}
\documentclass[12pt]{extarticle}
%Some packages I commonly use.
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{framed}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{amsfonts}
\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage[top=1 in,bottom=1in, left=1 in, right=1 in]{geometry}
\usepackage{tikz}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[english]{babel}
\usepackage{seqsplit}
\usepackage[nottoc]{tocbibind} 
\usepackage[utf8]{inputenc}

\newcommand{\cvec}[1]{{\mathbf #1}}
\newcommand{\murgg}{\Gamma(K^{ur}/K)}
\newcommand{\rvec}[1]{\vec{\mathbf #1}}
\newcommand{\ihat}{\hat{\textbf{\i}}}
\newcommand{\jhat}{\hat{\textbf{\j}}}
\newcommand{\khat}{\hat{\textbf{k}}}
\newcommand{\minor}{{\rm minor}}
\newcommand{\trace}{{\rm trace}}
\newcommand{\spn}{{\rm Span}}
\newcommand{\rem}{{\rm rem}}
\newcommand{\ran}{{\rm range}}
\newcommand{\range}{{\rm range}}
\newcommand{\mdiv}{{\rm div}}
\newcommand{\proj}{{\rm proj}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\co}{\mathcal{O}}
\newcommand{\GG}{\Gamma(K/\mathbb{Q})}
\newcommand{\spl}{split(f(x),\mathbb{Q})}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\renewcommand{\emptyset}{\varnothing}
\newcommand{\attn}[1]{\textbf{#1}}
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem*{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem*{note}{Note}
\newtheorem{exercise}{Exercise}
\newcommand{\bproof}{\bigskip {\bf Proof. }}
\newcommand{\eproof}{\hfill\qedsymbol}
\newcommand{\Disp}{\displaystyle}
\newcommand{\qe}{\hfill\(\bigtriangledown\)}
\newcommand{\lb}{\left(}
\newcommand{\rb}{\right)}
\newenvironment{polynomial}
  {\par\vspace{\abovedisplayskip}%
   \setlength{\leftskip}{\parindent}%
   \setlength{\rightskip}{\leftskip}%
   \medmuskip=4mu plus 2mu minus 2mu
   \binoppenalty=0
   \noindent$\displaystyle}
  {$\par\vspace{\belowdisplayskip}}
\setlength{\columnseprule}{1 pt}

\title{Unramified Extensions of Number Fields}

\date{April 2019}

\begin{document}
%!TEX root = ../main.tex
\maketitle
\begin{center}
{\large
Candidate Number 1006289

\bigbreak
MMath Mathematics Part C
\bigbreak
CCD Dissertations on a Mathematical Topic 
\bigbreak
Trinity Term 2019 
}
\end{center}

\pagebreak
\tableofcontents
\section{Goal}
This dissertation shows some of the techniques that have been used to find unramified extensions of number fields, the maximal unramified extension of number fields and also the structure of the Galois group of these extensions. Often, $K$ is taken to be a quadratic number field, and unramified extensions are defined by the splitting field of some polynomial $f(x) \in \Z[x]$. \par
In addition, this dissertation surveys the construction of unramified extensions of number fields, both finite and infinite. \par
This dissertation will focus on three topics: finding finite unramified extensions, infinite unramified extensions and maximal unramified extensions of number fields. \par
In addition, this paper uses computational mathematics packages to find concrete examples of number fields with interesting properties. The packages used are SageMath, Magma \href{http://magma.maths.usyd.edu.au/calc/}{http://magma.maths.usyd.edu.au/calc/} and the online database of number fields found at \href{https://hobbes.la.asu.edu/NFDB/}{https://hobbes.la.asu.edu/NFDB/} \cite{JONE2}.
 One important tool in the analysis of unramified extensions is bounds on the discriminant of a number field such bounds are given initially from Minkowski and then later from Odlyzko. \par
 Various results from Galois Theory, Algebraic Number Theory and Class Field Theory will be used in this paper.\par
 The reader of this paper is assumed to be familiar with all courses from Prelims, Part A and Part B and Part C. In particular, courses \textbf{B3.1 Galois Theory}, \textbf{B3.4 Algebraic Number Theory}, and all relevant courses on Group Theory. 




\section{Notation}
In the following notation, $K$ denotes a number field.
\begin{enumerate}
    \item $gcd(a,b)$ denotes the greatest common divisor of $a$ and $b$.
    \item $F_n$ denotes the $n^{th}$ Fibonacci number, where 
    $F_0 = F_1 = 1$ and $F_{n} = F_{n-1} + F_{n-2}$ for $n \geq 2$.
    \item $L_n$ denotes the $n^{th}$ Lucas number, where 
    $L_0 = 2$, $L_1 = 1$ and $L_{n} = L_{n-1} + L_{n-2}$ for $n \geq 2$.
    \item $D_n$ denotes the dihedral group of order $2n$.
    \item $S_n$ denotes the symmetrical group on $n$ elements.
    \item $Q_8$ denotes the quaternion group of order $8$.
    \item $h(K)$ is class number of $K$ and $Cl(K)$ is its ideal class group.
    \item $d_K$ or $\Delta(K)$ is the discriminant of $K$.
    \item $disc(f(x))$ denotes the discriminant of the polynomial $f(x)$.
    \item $K^{ur}$ is the maximally unramified extension of $K$
    \item $K^{tur}$ is the maximal tamely unramified extension of $K$.
    \item $n_K$ is the degree of the extension $K:\Q$.
    \item Let $N_{A/B}$ denote the relative norm for a number field extension $A/B$,
    \item $\bar{K}$ denotes the Galois closure of $K$.
    \item $KL$ denotes the compositum of two number fields $K$ and $L$.
    \item $rd_K$ is the root discriminant of $K$, $|d_K|^\frac{1}{n_K}$ .
    \item $G_K^{ur}$ is the Galois group $\Gamma(K^{ur}:K)$
    \item $C_K$ is the class field group of K. 
    \item $G^{ab}$ is the abelianisation of a group G, $G/[G,G]$
    \item $K_n$ is the $n_{th}$ term in the sequence defined by $K_0:=K$ and $K_{n+1}$ is the Hilbert class field of $K_n$.
    \item $K_H=\bigcup_{i}K_{i}$ is the Hilbert tower of $K$.  
    \item $\zeta_n$ is the $n_{th}$ root of unity. 
    \item A number field $K$ is said to be \textbf{unramified closed} if $K$ has no non-trivial unramified extensions. 
    \item A field extension is \textbf{strictly unramified} if it is not ramified at any finite or infinite prime.

\end{enumerate}
 Note that in general, decimal numbers are rounded to 2 decimal places. 
\section{Important Results in Group Theory, Algebraic Number Theory and Class Field Theory}

First, begin with some definitions and results from related areas of mathematics.   

\subsection{Group Theory}
\begin{lemma}
Suppose $n \geq 5$. Then $A_n$ and $S_n$ are not solvable. 
\end{lemma}
\begin{lemma}
Suppose $n$ is prime, and G is a transitive permutation group on $n$ letters , containing a transposition. Then $G$ is a symmetric group.
\end{lemma}

\subsection{Algebraic Number Theory}
Recall that a prime ideal $\mathfrak{p}$ in $\mathcal{O}_K$ factors in an extension $L$ of $K$ as
$\mathfrak{p}\mathcal{O}_L=\mathfrak{B}_1^{e_1}...\mathfrak{B}_m^{e_m}$, where $\mathfrak{B}_i$ are ideals in $\mathcal{O}_L$ intersecting $\mathcal{O}_K$ at $\mathfrak{p}$. \par
If $\mathfrak{p}$ is a prime ideal of $\mathcal{O}_K$, call $\mathfrak{p}$ a \textbf{finite prime}. This is in comparison to an \textbf{infinite prime}, which is determined by embeddings of $K$ in $\mathbb{C}$. \par 
Each $e_i\geq1$ and if $e_i>1$ for some $i$ then say that $\mathfrak{p}$ \textbf{ramifies} in $L$ and is unramified otherwise. If $e_i=1$ for all i then say $\mathfrak{p}$ \textbf{splits} in L. If there exists a unique prime $\mathfrak{B}$ lying over $\mathfrak{p}$ with inertial degree 1, then $\mathfrak{p}$ is \textbf{totally ramified} in $L$. \par


For an extension $L/K$, an infinite prime $\mathfrak{p}$ in $K$ is ramified in $L$ if it is real but has a complex extension to $L$. $L/K$ is an \textbf{unramified extension} if all primes are unramified, finite or not. 
\par
The following theorem motivates the definition of the maximal unramified extension of a number field. 
\begin{theorem}
The compositum of two finite unramified extensions of $K$ is also unramified, and so the union $K^{ur}$ of all unramified extensions is also an unramified extension of K. Furthermore, the residue field $\tilde{k}$ of $K^{ur}$ is the algebraic closure of the residue field $k$ of K.
\end{theorem}
\begin{proof}
    Suppose $K$ is a number field and $L,\tilde{L}$ are extensions of K. Let $\mathfrak{p}$ be an ideal unramified in both $L$ and $\tilde{L}$. Let $P$ be a prime lying over $\mathfrak{p}$ in $L\tilde{L}$. Let $M$ be the minimal normal extension of $L\tilde{L}$, i.e. the normal closure. Suppose $Q$ is a prime in $M$ lying over $P$, then  
    \begin{equation}
        \mathfrak{p}\subseteq P \subseteq Q
    \end{equation}
    Now define $E=E(Q|\mathfrak{p})$ denote the inertia group of $Q$ at $\mathfrak{p}$. 
    Since $\mathfrak{p}$ is unramified in $L$ and $\tilde{L}$, it follows that $Q \cap \mathcal{O}_L$ and $Q \cap \mathcal{O}_{\tilde{L}}$ are unramified in $L$ and $\tilde{L}$ respectively. 
 But the inertia field $M^E$ is the largest field in which $\mathfrak{p}$ is unramified, so it follows that $L\subseteq M^E$ and $\tilde{L} \subseteq M^E $, whence $L\tilde{L}\subseteq M^E$ and $\mathfrak{p}$ is unramified in $L\tilde{L}$.
\end{proof}
Following the definition of ramification, the next theorems show whether or not a prime ramifies.
\begin{theorem}
 Suppose that $K$ be a field extension of $\Q$ with discriminant D. Then a prime $p$
ramifies in $K$ if and only if $p|D$.   
\end{theorem}
Note that the discriminant of a number field is finite, hence only finitely many primes ramify over $\Q$. The following is an easy corollary:
\begin{corollary}
A field extension $K$ of $\Q$ ramifies at precisely one prime iff the absolute value of disc(K) is a prime power.
\end{corollary}
More generally, suppose $L/K$ is a field extension, and $\mathfrak{p}$ is a prime ideal in $K$. Then $\mathfrak{p}$ ramifies in $L$ iff it divides the relative discriminant $\Delta_{K/L}$. Also, $L/K$ is unramified iff the relative discriminant is the unit ideal. 
\begin{example}
    Suppose $f(x)= x^5 - x^3 - x^2 + x + 1$, and $K$ is the splitting field of $f$ over $\Q$. Then $\Delta(K)=-1609$, and $1609$ is prime, hence 1609 is the only prime which ramifies in $K$ over $\Q$. Note that f(x) is an irreducible quintic with precisely three real roots, meaning that $\GG \cong\ S_5$ and $K$ is an unsolvable extension of $\Q$.
\end{example}


Often it is important to find the Galois closure of a number field $K$; this is defined to be the smallest extension field, in terms of inclusion, which contains $K$ and is Galois over $\Q$. The following theorem is from Galois theory:
 \begin{theorem}
  Suppose $K=\Q(\alpha)$, where $\alpha$ is a root of an irreducible polynomial $f(x) \in \Z[x]$, then $\bar{K} = \spl$.
\end{theorem}


\subsection{Hilbert Class Fields}
Analysing the Hilbert class field - and hence the Hilbert class tower - gives information about unramified extensions of number fields. The \textbf{class
field tower problem} - stated by Hasse in 1925 - asks whether or not this tower is always finite, i.e. terminates in a field with class number one. The answer was shown to be negative when
Golod and Shafarevich found a counterexample in 1964. 
\begin{definition}
The \textbf{class field} of the trivial subgroup of C(K) is called the Hilbert class field of $K$. 
\end{definition}
\begin{definition}
$L/K$ is an \textbf{abelian extension} if it is a Galois extension and $\Gamma(L/K)$ is abelian. 
\end{definition}
The Hilbert class field is the maximal abelian extension of $K$ unramified at all primes of $K$, i.e. it is an unramified abelian extension of $K$, and contains every other unramified abelian extension of $K$. \par
The degree of its extension over $K$ is equal to the class number of $K$, and its Galois group is isomorphic to the ideal class group of $K$, taking Frobenius elements as prime ideals of $K$. \par
In particular, if $K$ is a unique factorisation domain then $K$ is equal to its own Hilbert class field. 
Here are three further examples:
\begin{example}
    Suppose K=$\Q$. Then $K$ is its own Hilbert class field.
    \label{ex:q_is_ufd} 
\end{example}
\begin{example}
    Suppose $K=\Q\left(\sqrt{-15}\right)$, and take $L=\Q\left(\sqrt{-3},\sqrt{-5}\right)$. $\Delta(K) = -15$ and $\Delta(L) = -15^2$, so $L$ is an degree 2 unramified abelian extension of $K$. In addition, $h(K)=2$, so indeed $L=K_1$.  
\end{example}
\begin{example}[Hasse]
    Suppose $K=\Q\left(\sqrt{-31}\right)$ with class number 3. Let $L$ be its Hilbert class field. Then $L = \Q(\alpha)$, where $\alpha$ is a root of the polynomial 
    \begin{equation}
        x^3+\frac{3+\sqrt{-31}}{2}x^2+\frac{-3+\sqrt{-31}}{2}x -1 =0.
    \end{equation}
\end{example}

Finally, define the \textbf{narrow class field}.
\begin{definition}
Suppose $K$ is a $\Q$ - extension. Recall that the class field cl(K) is $C_K = I_K/P_k$ , where $I_K$ is the group of fractional ideals of $K$ and $P_K$ is the group of principle fractional ideals of $K$. \par

The \textbf{narrow class field} $C_K^{+}$ is defined by $C_K^{+} = I_K/P_K^{+}$, where $P_K^{+}$ is the group of totally positive principal fractional ideals of $K$, i.e ideals of the form $a\mathcal{O}_K$, where $a$ is an element of $K$ such that $\sigma(a)$ is positive for every embedding $\sigma: $K$ \rightarrow \R$. \par
Note that the \textbf{narrow class number} is equal to $|C_K^{+}|$ and is denoted by $h^{+}(K)$. 
  The ideal class group is a quotient of the narrow class group, implying that the narrow class number is a multiple of the class number. When the number field is totally complex, they are equal. 


\end{definition}
\subsection{p-class fields}
\subsubsection*{Definitions}
The following definitions and corollaries will be useful in determining the structure of the Hilbert class field. 
\begin{definition}
A \textbf{p-group} is a group in which every element has order equal to a power of $p$.
\end{definition}
\begin{definition}
A \textbf{p-extension} $L$ of a number field $K$ is an extension where the Galois group is a p-group.
\end{definition}

\begin{definition}
A \textbf{Hilbert p-class field} $H_K^{p}$ of a number field $K$ is the maximal unramified abelian p-extension of K, with the \textbf{p-class field tower} defined in a similar way to the definition of the Hilbert tower. 
\end{definition}

\subsubsection{ p-class Field Towers }
\begin{corollary}
 A number field $K$ can be embedded into a finite field extension with class number coprime to $p$ iff the Hilbert p-class field tower terminates.
\end{corollary}
\begin{corollary}
If any p-class field tower over $K$ is infinite, then the class field tower is also infinite. If the p-class tower terminates, then $H_{K_\infty}^{p}$ is a finite field extension of $K$ and $\Gamma(H_{K_\infty}^{p}/K)$ is a p-group. \label{cor:p-class}
\end{corollary}
Note that the converse to the first part of \Cref{cor:p-class} need not hold; a counterexample is given in Schoof \cite{SCHO}. Consider $\Q\left(\sqrt{-239},\sqrt{4049}\right)$. Then this biquadratic field extension of $\Q$ has an infinite class field tower, but all its p-class field towers are finite.
\section{Bounds on Discriminants}
\subsection{Root Discriminant}
One technique for calculating $K^{ur}$ is to use bounds on the root discriminant of a number field. Since unramified extensions have the same root discriminant, these bounds can prove that an unramified extension of a number field with class number one is indeed the maximal unramified extension. Minkowski first found a lower bound for the discriminant using geometry and Odlyzko later improved these bounds. Assuming the Generalised Riemann Hypothesis, even stronger bounds can be achieved. \par
In Neukirch's Algebraic Number Theory textbook \cite{NEUK}, the following theorem for the relative discriminant is stated. 
\begin{proposition}
Let $K,L,M$ be number fields with the inclusions $ K \subset $L$ \subset M 
$. Then \begin{equation}
    \Delta_{L/K} = N_{L/K}(\Delta_{L/K})\Delta_{L/K}^{[L:K]}
\end{equation} \label{prop:rd}
\end{proposition}
\begin{corollary}
 If $L$ is an unramified extension of K, then $\Delta_{L/\Q}= \Delta_{L/\Q}^{[L:K]}$. Furthermore, $L$ and $K$ have the same root discriminant.
\end{corollary}
\begin{proof}
Since $L$ is an unramified extension of K, no prime divides $\Delta_{L/K}$, so $\Delta_{L/K}$ is the unit ideal. But then $N_{K/\Q}(\Delta_{L/K})=1$ and so the result follows by the tower law and \Cref{prop:rd}, \begin{equation}
    rd_L=\Delta_{L/\Q}^\frac{1}{[L:K][K:\Q]}=\Delta_{K/\Q}^\frac{1}{[K:\Q]}= rd_K
\end{equation}
Hence if $L$ is an unramified extension of K, a rational prime $p$ divides $\Delta(K)$ iff $p$ divides $\Delta(L)$.
\end{proof}
\subsection{Minkowski's Bound}
\subsubsection*{Statement}
Minkowski's theorem gives another bound for the root discriminant, derived from the geometry of numbers:

\begin{theorem}
If $K$ is a number field with $r_1$ real and $2r_2$ complex conjugate fields, and $n=r_1+2r_2$ is the degree of the field, then 
\begin{equation}
|d_K| \geqslant \left( \dfrac{\pi}{4}\right)^{2r_2} \left( \dfrac{n^n}{n!}\right)^2.
\end{equation}
\end{theorem}





Taking $n^{th}$ roots gives a bound for the root discriminant:
\begin{equation}
rd_K\geqslant (\dfrac{\pi}{4})^{\frac{2r_1}{n}}\dfrac{n^2}{n!^{\frac{2}{n}}}.
\end{equation} 

\subsubsection*{Number Fields with No Unramified Extension}
As shown in \Cref{ex:q_is_ufd}, every nontrivial field extension of $\Q$ is ramified. Therefore $\Q^{ur} = \Q$. In the answer given by Conrad at \cite{CONRAD}, Minkowski's bound is used to find more examples of such number fields.
\begin{theorem}
Suppose $K$ is a number field of degree $m$, and define $f(n) = \left(\dfrac{\pi}{4}\right) \dfrac{n^2}{n!^{\frac{2}{n}}}$. Suppose $rd_K \leq f(2m)$, then $K$ is unramified-closed.
\label{thm:mink_bound}
\end{theorem}
\begin{example}
Suppose $m=2$, then $f(4) = 2.57$, and so $\Q(\sqrt{-1})$ and $\Q(\sqrt{-3})$, $\Q(\sqrt{-5})$ all satisfy \Cref{thm:mink_bound}, so have no nontrivial unramified extensions.  
\end{example}
Furthermore, suppose $K$ is a quadratic number field with (wide) class number equal to 1 and with $f(5) > rd_k > f(4)$. Then any unramified extension of $K$ must be a quadratic extension. However, such an extension would be a nontrivial abelian extension unramified at no finite places, with contradiction. This argument shows that $\Q(\sqrt{-2})$ and $\Q(\sqrt{-7})$ are also unramified-closed. 

\begin{example} 

For $m=3, f(6) = 3.15$. The number fields defined by $x^3-x^2+1$ and $x^3+x-1$, which both have Galois groups isomorphic to $S_3$, also satisfy the theorem and are unramified-closed.
\end{example}
\begin{example} 

For $m=4, f(8) = 3.55$. Then let $K_1$ be defined by $x^4 - x^3 - x^2 + x + 1$, $K_2$ be defined by $x^4 - x^3 + x^2 - x + 1$, $K_1$ be defined by $x^4 - x^2 + 1$. Then $K_1$, $K_2$ and $K_3$ are all unramified-closed, and have Galois groups isomorphic to $D_4$, $C_4$ and $V_4$ respectively. 
\end{example}


As $n\rightarrow \infty$, Stirling's formula can estimate $f(n)$, showing that
\begin{equation}
    \lim_{n\to\infty} f(n) = \frac{\pi e^2}{4} = 5.80
\end{equation}
Furthermore, $f(n)$ is increasing, so this direct argument from Minkowski's bound can only prove that a field is unramified closed if the root discriminant is less than $5.80$. 

\cite{JONE2} gives a total of 224 number fields with root discriminant less than $ \frac{\pi e^2}{4}$, and the largest degree of all these fields is $8$. For $n=5$, the smallest root discriminant is $4.38 > 3.82 = f(8)$, and \Cref{thm:mink_bound} cannot be applied. Similar results hold for $n = 6,7,8$. Therefore \Cref{thm:mink_bound} cannot be applied directly to any other number fields. 
\subsection{Odlyzko's Bound}
\subsubsection*{Statement}
Odlyzko's bound \cite{ODL1990} improved on the Minkowski's bounds for the root discriminant. for the discriminant of a number field. It can be stated as  
\begin{equation}
\label{eqn:odlyzko}
rd_K\geqslant 60^{\frac{r_1}{n}}22^{\frac{r_2}{n}}+o(1)\:as\:n\rightarrow \infty   
\end{equation}
Moreno \cite{MORENO} writes this bound explicitly as 
%todo find citation
\begin{equation}
rd_K\geqslant 60^{\frac{r_1}{n}}22^{\frac{r_2}{n}}\exp\left(-8.6n^{-2/3}\right) \label{Moreno}
\end{equation}
Furthermore, under the assumption of the Generalised Riemann Hypothesis, 
this bound can be improved by replacing the numbers 60 and 22 by 188 and 41 respectively. 
\subsubsection*{Using Odlyzko's Bound}
Following Yamamura \cite{YAMA1986}, write this bound function as $B(n,r_1,r_2)$. The following theorem will show how to use the lower bound on the root discriminant to prove than an unramified extension of a number field is maximal
\begin{theorem}
Suppose that $K$ is a degree $n$ number field with $r_1$ real places and $2r_2$ complex places. Let $B(n,r_1,r_2)$ is the lower bound for $rd_K$, and suppose $L$ is an unramified normal degree extension of $K$ of degree $m$. If $h(L)=1$, and

\begin{equation}
        rd_K<B(60 \cdot m \cdot n_K,60 \cdot m \cdot r_1,60 \cdot m \cdot r_2),
    \end{equation}
    then $K^{ur}=L$.
\end{theorem}
\begin{proof}
Suppose $M$ were an unramified nontrivial normal extension of $K$. Since the compositum retains closure and unramified extensions, $LM$ is also a normal unramified extension of $L$. Define $G=\Gamma(LM/L)$ with $|G|=a$. \par 
If $G$ had a normal subgroup $H$, the Fundamental Theorem of Galois Theory would imply that $G/H$ would correspond to an Abelian unramified extension of $L$, contradicting $h(L)=1$. Hence $G$ is unsolvable. This immediately implies that $a\geqslant 60 = |A_5|$ because $A_5$ is the smallest unsolvable group.\par
Since $LM$ is also an unramified extension of $K$, 
\begin{equation} 
    rd_{LM}=rd_{K}\ < B(60 \cdot m \cdot n_K,60 \cdot m \cdot r_1,60 \cdot m \cdot r_2)\leq B(a \cdot m \cdot n_K,a \cdot m \cdot r_1,a \cdot m \cdot r_2) \label{odlyzko} \tag{*} 
\end{equation} 
But $LM/\Q$ has $a \cdot r_1 \cdot m$ real places and $2 \cdot a \cdot r_2 \cdot m$ complex places, so $[LM:\Q] = a \cdot m \cdot n$, contradicting \Cref{odlyzko}. Hence $L$ is unramified-closed and $L=K^{ur}$. 
\end{proof}
Applying this result to \Cref{Moreno} gives the following corollary:
\begin{corollary}
Suppose $K$ is a degree $n$ number field with signature $(r_1,r_2)$, and $L$ is a degree $m$ unramified extension of $K$ with trivial class group. If 
\begin{equation}
rd_K< 60 ^{\frac{r_1}{n}} 22 ^{\frac{r_2}{n}} \exp\left(\frac{-8.6}{60\cdot m \cdot n}\right),
\end{equation}
then $L=K^{ur}$. 
\end{corollary}

\section{Unramified Extensions of Number Fields}
Kim \cite{KIM2015} showed that given any finite solvable group $G$, there exist infinitely many abelian extensions $K/\Q$ and Galois extensions $M/\Q$ such that $\Gamma(M/K) \cong G$ and $M/K$ is unramified. However, it is interesting to either find explicit examples of infinite families of number fields with finite solvable extension, or to find number fields with unramified unsolvable extension. 
\subsection{Kondo's Results}
In the paper by Kondo \cite{KOND}, conditions are given for the splitting field of a polynomial to be an unramified extension of the quadratic field defined by the square root of its discriminant.
\begin{theorem}
    Suppose $F$ is a number field with discriminant $\Delta(F)$ of degree $n$, and $K$ is its Galois closure over $\Q$. Suppose $\Delta(F)$ is not a square, i.e. it is equal to the discriminant of the quadratic number field $\Q(\sqrt{\Delta(F)})$, then \begin{enumerate}
        \item $\Gamma(K/\Q)\cong S_n$
        \item $K/\Q(\sqrt{\Delta(F)})$ is an unramified extension.
    \end{enumerate}
\end{theorem}
Kondo also gives this theorem:
 \begin{theorem}
 \label{thm:tfae}
    The following are equivalent: \begin{enumerate}
        \item $\Delta(F)$ is equal to the discriminant of the quadratic number field $\Q(\sqrt{\Delta(F)})$
        \item For every prime dividing $\Delta(F)$, its ideal $\mathfrak{p}$ in $F$ has precisely one ramified divisor.
    \end{enumerate}
\end{theorem}
\begin{lemma}
Furthermore, the following condition is equivalent to conditions of \Cref{thm:tfae}:
\par
    The inertia group of every ramified prime of $K$ is a group of order 2 generated by a transposition.\par

In particular, if $F$ satisfies this condition, then $\Delta(F)$ is equal to $\Delta(\Q(\sqrt{\Delta(F)})$.
\label{lem_trans}
\end{lemma}
\begin{proof}
This is immediate from a theorem of Van der Waerden \cite{WAER}. 
\end{proof}
\begin{lemma}
\label{lem_tfae}
Suppose $\Delta(F)\notin \Q^2$. Then the following are equivalent:\begin{enumerate}
    \item $K$ is an unramified extension of $\Q(\sqrt{\Delta(F)})$
    \item The inertia group of every ramified prime of $K$ is a group of order 2, generated by an odd permutation. 
\end{enumerate}
\end{lemma} 
The following examples were found using SageMath:
\begin{example}
Define $f(x)=x^6 + x^5 - 6x^4 - 4x^3 + 8x^2 + 3x - 2$. Also define $F=\Q(\theta)$, where $\theta$ is a root of f, and let $K$ be the splitting field of f over $\Q$. Then $d(f)=\Delta(F)=7846061=17^3.1597$. 
\begin{equation}
   f(x)= (x^3 + 9x^2 + 16x + 7)^2\:mod\:17
\end{equation}
By \Cref{lem_trans} and \Cref{lem_tfae} indeed $K$ is an unramified extension of $\Q(\sqrt{17^3 \cdot 1597})$. Furthermore, $\Gamma(K/\Q)$ is a group of order 72 and is isomorphic to the wreath product of $S_3$ by $C_2$. \par 
It follows that $K/\Q(\sqrt{17^3 \cdot 1597})$ is an unramified extension with Galois group isomorphic to the Frobenius group of order 36.
\end{example}
\begin{example}
\label{ex:frob}
 Let \begin{equation}
     f(x)=x^7 + 2x^6 - x^5 - x^4 + x^3 - x^2 - x + 1
 \end{equation}and $F$ and $K$ be as in \Cref{ex:frob}.
Then $disc(f)=\Delta(F)=-357911=-71^{3}$ and
\begin{equation}
    f(x)=(x + 19)(x + 42)^2 (x + 59)^2(x + 68)^2\:mod\:71.
\end{equation}
Therefore, by \Cref{lem_tfae}, $K/\Q(\sqrt{-71})$ is unramified. The Galois group of $K/\Q$
is isomorphic to $D_{7}$, and so $K/\Q(\sqrt{-71})$
is an unramified extension with Galois group isomorphic to $C_7$.
Since $h(\Q(\sqrt{-71}))=7$, this shows that $K$ is the absolute class field of $\Q(\sqrt{-71})$
\end{example}
\begin{example}
    Suppose a polynomial $f$ is defined with the following properties: \begin{equation}
        f(x) =x^9 - x^8 - 2x^7 + x^6 + 2x^5 + x^3 + x^2 - x - 1
    \end{equation} \par
    \begin{equation}
        disc(f)= \Delta(F)=66078977=23^3 \cdot 5431
    \end{equation} 
    \begin{equation}
        f(x)\equiv(x^3 + 8x^2 + 18x + 1)(x^3 + 7x^2 + 3x + 1)^2\:mod\:23.
    \end{equation}
Therefore $K/\Q(\sqrt{-23})$ is unramified. $\Gamma(K/\Q)$ is isomorphic to the wreath product of $S_3$ by $S_3$ and has order $1296=2^3 \cdot 3^3$, whence $K/\Q(\sqrt{-23})$ has Galois group of order $648$.
\end{example}

\subsection{Quintic Polynomials}
%todo check this, write conditions explicitly
In \cite{yamamura1986}, Yamamura states the following theorem, which gives a method of finding infinitely many real quadratic number fields with an unramified (and unsolvable) $A_5$ - extension. 
\begin{theorem}
    Suppose $S_1$ and $S_2$ are finite sets of primes satisfying $S_1 \cap S_2 = \emptyset$ and $2,5 \notin S_2$. Then there exist infinitely many real quadratic number fields with the following properties: \begin{enumerate}
        \item $F$ is a strictly unramified $A_5$ - extension.
        \item All primes in $S_1$ are unramified in $F$.
        \item All primes in $S_2$ are ramified in $F$.
      
    \end{enumerate}  \label{thm:yama_ramifying}
\end{theorem}
To prove this theorem, Yamamura gives the following five conditions for a quintic polynomial of the form \begin{equation}
    f(x)=x^5-2ax^3+bx+c: a,b,c \in \Z
\end{equation} with the properties
\begin{enumerate}
\item f(x) is irreducible over $\Q$.
\item $b \equiv c \equiv 1 \: mod \: 2  $.
\item All the roots of $f(x)$ are real.
\item Define $D = disc(f)$, and define
$A= 5ac^2(3a^2-5b)+8b^2(a^2-b^2)$
$B = 125ac^2-16b(a^2-b)(6a^2-5b)$.
Then any prime factor of $(A,B,D)$ is also a prime factor of $2ac$. 

\item $gcd(a,b,5) =gcd((a^2b-b^2),c,D)=1$.
{}
\end{enumerate} 

\begin{lemma}
Suppose $f$ has these properties. Then $\Q(\sqrt{D})$ is a real quadratic number field, and the splitting field $K$ of $f(x) $ is a strictly unramified $A_5$ - extension of $\Q(\sqrt{D})$. 
\end{lemma}
\begin{example}
    The following example was found using SageMath. Take $a=81,b=57,c=13$. Then $f(x) = x^5-162x^3+57x+13$ with splitting field $K$ and $D= disc(f) = 19 \cdot 587 \cdot 510172213$, whence the splitting field $K$ is an unramified $A_5$ - extension of $\Q(\sqrt{D})$. 
\end{example}
In Yamamura's paper, the following polynomial is defined with certain modularity conditions: 
\begin{equation}
f_m(x)= x^5-2m^2x^3+(6m^2-1)x-(m-4)
\end{equation}
  for some integer $m$. Imposing the modularity conditions on $m$ means that $f_m(x)$ meets criteria $(2)$ and $(3)$ from \Cref{thm:yama_ramifying}, thereby producing such a family of quintic polynomials. \par
Yamamura also gives examples of real quadratic number fields with class number one having either a strictly or weakly unramified $A_n$ - extension which is an $S_n$ - extension of $\Q$ for $n$ equal to 5, 6, and 7. 
\begin{example}
As Hunter shows \cite{HUNTER}, the minimum possible discriminant of a quintic field with one real and two pairs of imaginary conjugate fields is $1609$. 
Taking $K=\Q(\sqrt{1609})$, $h^{+}(K)=1$ and $K$ has a weakly unramified $A_5$ - extension.
\end{example}
A further sextic example is found using by using the database of number fields maintained by Jones and Roberts at \cite{JONE2}:
\begin{example}
Suppose $K=\Q(\sqrt{592661})$, then $K$ has a strictly ramified $A_6$ - extension, defined by the splitting field of $x^6 - x^5 - 5x^4 + 4x^3 + 5x^2 - 2x - 1$. 
%todo find citation and add to bib
\end{example}


\subsection{Unramified Extensions of Number Fields defined by a Trinomial}

Uchida \cite{uchida1970} gives the following theorem about the ramification of primes in number fields defined by trinomials:
\begin{theorem}
Suppose $K$ is a number field of finite degree with integers $a$ and $b$, \\ 
$f(x) = x^n-ax+b$ and $L$ is the splitting field of $f(x)$ over $K$. If $(n-1)a$ and $nb$ are relatively prime, the ramification index of any prime ideal of $L$ over $K$ is either 1 or 2.  \label{thm:uchida_index}
\end{theorem}

This theorem has the following easy corollary:
\begin{corollary}
Suppose $f(x) \in \Q[x]$, with discriminant $D$, and every prime factor in the factorisation of D appears odd times. Let $K$ be the splitting field of $f(x)$ over $\Q$. Then $K/\Q\left(\sqrt{D}\right)$ is unramified. \label{cor:uchida}
\end{corollary}
\begin{proof}
Suppose $p$ is a rational prime ramified in $K/\Q$. Then $p|D$. However, $p$ ramifies in $\Q(\sqrt{D})/\Q$, with ramification index 2. Therefore $p$ is unramified in $K/\Q(\sqrt{D})$. 
\end{proof}
Uchida also gives the following examples of unramified extensions of quadratic number fields with Galois group isomorphic to $A_n$.\par
\begin{example}
Define $f_n(x) = x^n-x+1$ with discriminant $\mathfrak{d}_n$. First note that for all $n \in \Z$, 
$gcd((n-1)a, nb) = gcd(n-1,n) =1 $. Calculating the discriminant gives
\begin{equation}
\label{eq:disc_trin}
disc(x^n-ax+b) = n^nb^{n-1}-(n-1)^{n-1}a^n
\end{equation}
 and so $\mathfrak{d}_n = n^n-(n-1)^{n-1}$. For $n \in \{5,6,7\}$, $\mathfrak{d}_n$ is either prime or the product of two primes, hence $f_n(x)$ satisfies the criteria of \Cref{thm:uchida_index}. Now 
\begin{equation}
x^5 - x+1 \equiv (x^2 - x +1)(x^3 +x^2 +1)\:mod\:2
\end{equation}
hence the Galois group defined by $f_5(x)$ is isomorphic to $S_5$. Similar arguments hold for $n=6$ and $n=7$. Therefore there exist unramified extensions of quadratic number fields with $D_5$, $D_6$, $D_7$ or $S_5$, $S_6$, $S_7$ as Galois groups. 
\end{example}


Now consider another family of trinomials.
\begin{definition}
\label{def:irred_trin}
Define $F_n(x) = x^n-x-1$ (note the change in sign) for $ n \in \N$ with discriminant $\mathfrak{D}_n$ and splitting field $L_n$.
\end{definition}

  Selmer \cite{SELMER} shows that for $n>1$, $F_n(x)$ is always irreducible. Furthermore, by \Cref{eq:disc_trin}, $\mathfrak{D}_n= (-(n-1))^{n-1} - (-n)^{n}$. \par 
Using SageMath, the factorisation of $\mathfrak{D}_n$ is calculated for $2 \leq n \leq 30$. Define $G_n$ be the Galois group defined by $F_n(x)$. Using the Magma package available at \url{http://magma.maths.usyd.edu.au/calc/}, the Galois group $G_n$ is calculated and the data is presented in the following table:
\begin{center}
 \begin{tabular}{||c | c | c | c||} 
 \hline
 $n$ & $gcd((n-1)a,nb)$ & $G_n$ & Factorisation of $|\mathfrak{D}_n|$ \\ [0.5ex] 
 \hline\hline
2 & 1 & $S_{2}$ & $5$ \\
\hline
3 & 1 & $S_{3}$ & $23$ \\
\hline
4 & 1 & $S_{4}$ & $283$ \\
\hline
5 & 1 & $S_{5}$ & $19 \cdot 151$ \\
\hline
6 & 1 & $S_{6}$ & $67 \cdot 743$ \\
\hline
7 & 1 & $S_{7}$ & $776887$ \\
\hline
8 & 1 & $S_{8}$ & $11 \cdot 1600069$ \\
\hline
9 & 1 & $S_{9}$ & $7 \cdot 11 \cdot 13 \cdot 43 \cdot 79 \cdot 109$ \\
\hline
10 & 1 & $S_{10}$ & $173 \cdot 60042893$ \\
\hline
11 & 1 & $S_{11}$ & $275311670611$ \\
\hline
12 & 1 & $S_{12}$ & $1237 \cdot 7438489991$ \\
\hline
13 & 1 & $S_{13}$ & $28201 \cdot 10423708597$ \\
\hline
14 & 1 & $S_{14}$ & $31 \cdot 59 \cdot 1279 \cdot 4879633159$ \\
\hline
15 & 1 & $S_{15}$ & $52489 \cdot 418511 \cdot 19428121$ \\
\hline
16 & 1 & $S_{16}$ & $227 \cdot 246027323 \cdot 338142271$ \\
\hline
17 & 1 & $S_{17}$ & $808793517812627212561$ \\
\hline
18 & 1 & $S_{18}$ & $773 \cdot 1153064743 \cdot 45072130459$ \\
\hline
19 & 1 & $S_{19}$ & $5 \cdot 659 \cdot 588489604729898953429$ \\
\hline
20 & 1 & $S_{20}$ & $47 \cdot 233 \cdot 443 \cdot 22022174223585405703$ \\
\hline
21 & 1 & $S_{21}$ & $1137694897331 \cdot 5043293621028391$ \\
\hline
22 & 1 & $S_{22}$ & $5 \cdot 69454092876521107983605569601$ \\
\hline
23 & 1 & $S_{23}$ & $29 \cdot 53264767 \cdot 13296646221023838475181$ \\
\hline
24 & 1 & $S_{24}$ & $101 \cdot 2347 \cdot 5714547093403974893094772369$ \\
\hline
25 & 1 & $S_{25}$ & $10667 \cdot 282401201 \cdot 925997749 \cdot 31362479733103$ \\
\hline
26 & 1 & $S_{26}$ & $73 \cdot 181 \cdot 2385857 \cdot 32375941061 \cdot 6118709648547401$ \\
\hline
27 & 1 & $S_{27}$ & $23 \cdot 3539 \cdot 535391 \cdot 10033918834509020645502251401$ \\
\hline
28 & 1 & $S_{28}$ & $349 \cdot 14769635993383 \cdot 6516302002526983353692617$ \\
\hline
29 & 1 & $S_{29}$ & $41393681953973 \cdot 61230132484136034758796880121$ \\
\hline
30 & 1 & $S_{30}$ & $4421 \cdot 22659339443160463 \cdot 2080906233684319160584903$ \\
\hline


\end{tabular}
\end{center}


Hence for $2 \leq n \leq 30$, the criteria given in \Cref{cor:uchida} are fulfilled, and there exist unramified extensions of quadratic number fields with Galois groups isomorphic to $A_n$ or $S_n$ for all such $n$. For $n \geq 5$, these groups are unsolvable, in contrast to the results from Kim \cite{KIM2015}.
\par
\subsubsection*{A Remark on Uchida's Results on Trinomials}
Yamamoto \cite{YAMA1970} gives the following classification of trinomials of the form in \Cref{thm:uchida_index}:
\begin{theorem}
Suppose $f(x)$ is trinomial of degree $n$ of the form in \Cref{thm:uchida_index} with splitting field $L$. If the following conditions hold: 
\begin{enumerate}
    \item $(n-1)a$ and $nb$ are relatively prime 
    \item $\Gamma(L/\Q) \cong S_n$.
\end{enumerate}\par
Then $K$ is an $A_n$ - extension of $\Q\left( \sqrt{disc(f)}\right)$ which is unramified at all finite primes. \label{thm:yama_trinomial}
\end{theorem}

Uchida \cite{uchida1970} gives the following proposition:
\begin{proposition}
Suppose $f(x)=x^n+ax+b$ is a trinomial with splitting field $L$, and 
\begin{enumerate}
\item $n$ is prime.
\item $gcd((n-1)a,nb)=1$.
\item $f(x)$ is irreducible.
\end{enumerate}
Then $\Gamma(L/\Q) \cong S_n$. \label{prop:uchida}
\end{proposition}
Putting the remark from Selmer \cite{SELMER} that $x^n-x-1$ is irreducible, \Cref{thm:yama_trinomial} and \Cref{prop:uchida} together, the following corollary can be stated:
\begin{corollary}
Suppose $F_p(x)=x^p-x-1$ is in \Cref{def:irred_trin} with $p$ prime, and with splitting field $L_p$. Then $G_p \cong S_p$ and $\Gamma\left(L_p/\Q\left(\sqrt{\mathfrak{D}_p}\right)\right)\cong A_p$. Thus for $p \geq 5$, $F_p$ defines a family of unramified unsolvable extensions of imaginary quadratic number fields. 
\end{corollary}
\subsection{Yamamoto's Constructions of Unramified Extensions of Number Fields Defined by Trinomials}
In addition, Yamamoto states another theorem:
\begin{theorem}
If there exist primes `'$p_1, p_2, p_3$ such that \begin{itemize}
\item $f(x)$ is irreducible modulo $p_1$
\item $f(x)$ is the product of a degree 1 irreducible polynomial and a degree $n-1$ irreducible polynomial modulo $p_2$
\item $f(x)$ is the product of $n-2$ distinct degree 1 polynomials and a degree 2 irreducible polynomials modulo $p_3$
\end{itemize}
Then the Galois group defined by the splitting field of $f$ is isomorphic to $S_n$.

\end{theorem}

\begin{example}
\label{ex:trinomials}
Set $f(x)= x^5+51x-95$ with discriminant $D$, then $f(x)$ is irreducible modulo 1979, i.e. 
\begin{equation}
f(x)\equiv x^5+51x-9 \: mod  \: 979
\end{equation}
\begin{equation}
f(x) \equiv(x + 357)(x^4 + 1642x^3 + 1512 x^2 + 1945x + 1338) \:mod\: 1999,
\end{equation}
\begin{equation}
f(x) \equiv(
x + 194)(x + 384)(x + 1332)(x^2 + 1832x + 950)\:mod\:1871
\end{equation}
 Let $L$ be the splitting field of $f$, and $K = \Q\left(\sqrt{disc(f)}\right)$. 
Note that 
\begin{equation}
gcd((n-1)(a),nb) = gcd(204,-475)=1
\end{equation}
 and 
\begin{equation}
D = 342859667381 = 7^3 \cdot 11 \cdot 1567 \cdot 57991.
\end{equation} 

Therefore $\Gamma(L,\Q) \cong S_5$ and $L$ is an $A_5$ - extension of $K$ unramified at all finite primes.
\end{example}

Using SageMath, additional examples were found. For instance: 
\begin{example}
Set $f(x)= x^6-23x-58$ with $D$, $K$ and $L$ as in \Cref{ex:trinomials}, and $p_1,p_2,p_3$ are equal to $1999$, $1987$, $1861$ respectively. \par
Calculating the greatest common divisor gives 

$gcd((n-1)a,nb) = gcd(-115,-324)=1$, $f(x)$ is irreducible mod 1999,
\begin{equation}
f(x) \equiv(x + 1818)(x^5 + 169x^4 + 743x^3+386x^2+1650x+647)\: mod \:1987
\end{equation}
\begin{equation}
f(x) \equiv(x + 37)(x + 406)(x + 1265)(x+1396)(x^2 + 618 + 1485)\:mod\:1861
\end{equation}
 Also $D = 31085593520933 = 7 \cdot 617 \cdot 7197405307$. 

 Therefore, $\Gamma(L/\Q) \cong S_6$ and $L$ is an $A_6$ - extension of $K$, unramified at all finite primes.
\end{example}
\subsection{Infinite Family of Real Quadratic Fields with Class Number a Multiple of 3}
In the paper by Uchida \cite{uchida1970}, further examples are given; for example $x^7-x+1$, $x^9-x+1$ and $x^{10}-x+1$. 
Applying the initial theorem in the case that $n=3$, Uchida also uses unramified extensions to prove that there exist infinitely many real quadratic number fields with class numbers divisible by 3:
\begin{proof}
Suppose $f(x) = x^3+ax+b$ is an irreducible cubic with splitting field $K$ and discriminant $D$, such that $\Gamma(K/\Q) \cong S_3$. Then $K/\Q(\sqrt{d})$ is unramified and the class number of $\Q(\sqrt{d})$ is divisible by 3. \par

Fixing $b=1$, it suffices to find infinitely many different $\Q(\sqrt{D})$ with positive $D$. Picking a prime $p \equiv 2$ mod 3 with $a_1 \equiv 1$ mod 3 and $a_1 > 2$ such that $p | 4a_1^3 - 27$ will generate the required fields. Examples of such fields have been calculated using SageMath and are tabulated below. Note that for $D=9410521,32969605$, the class group is not cyclic. 
\begin{center}
 \begin{tabular}{| c | c | c | c |}
 \hline
p & $a_1$ & D & $Cl(\Q(\sqrt{D})$  \\ 
\hline
5 &  7 & 1345 & $C_{6}$ \\
\hline
11 &  16 & 16357 & $C_{3}$ \\
\hline
17 &  46 & 389317 & $C_{12}$ \\
\hline
23 &  70 & 1371973 & $C_{3}$ \\
\hline
29 &  10 & 3973 & $C_{6}$ \\
\hline
41 &  28 & 87781 & $C_{12}$ \\
\hline
47 &  55 & 665473 & $C_{21}$ \\
\hline
53 &  133 & 9410521 & $C_{6} \times C_{2}$ \\
\hline
59 &  175 & 21437473 & $C_{6}$ \\
\hline
71 &  109 & 5180089 & $C_{3}$ \\
\hline
83 &  241 & 55990057 & $C_{6}$ \\
\hline
89 &  202 & 32969605 & $C_{18} \times C_{2}$ \\
\hline
\end{tabular}
\end{center}
%todo find way to enumerate groups 
%todo check this 
\end{proof}


\subsection{Unramified Cyclic Quintic Extensions of Imaginary Quadratic Number Fields}


Kishi \cite{KISH} finds an infinite family of imaginary quadratic number fields with class number a multiple of 5, and also a family of unramified cyclic quintic extensions of these fields. 

 For a non-negative integer $m$, define 
\begin{itemize}
\item $k_m = \Q(\sqrt{-F_{2m+1}})$ 
\item $ g_m(x) = x^5 - 10x^3  -20x^2 + 
    5(20F^2_{2m+1} - 3)x
    + 40F^2_{2m+1}((-1)^{m}L_{2m+1} + 1)- 4$
\item $\zeta = e^{\frac{2\pi}{5}}$ and 
\item $\phi = \dfrac{1+\sqrt{5}}{2}$
\item $\delta_m = 1+\phi^m(\sqrt{-F_{2m+1}})(\zeta-\zeta^{-1})$

\end{itemize}

Then there exists a unique proper sub-extension, $M$, of the bi-quadratic
extension \\ $k(\zeta)/\Q(\sqrt{5})$ which is not equal to 
$k(\sqrt{5})$ or $\Q(\zeta)$, denoted by $M$. Then $M$ is a cyclic quartic field. \par 
Define 
\begin{itemize}
\item $NT(\alpha) = N_{\Q(\sqrt{5})}(\alpha)Tr_{M/\Q(\sqrt{5})}(\alpha)$
\item $\tau$ is the generator of $\Gamma(k(\zeta)/k)$ with $\zeta^2=\zeta^\tau$
\item For $\gamma \in M$, define the polynomial 
\begin{equation}
\begin{split}
    f_\gamma(x) = {} & x^5 - 10N_M(\gamma)x^3  -5N_M(\gamma)NT (\gamma)x^2 \\ &
  + 5N_M(\gamma)(N_M(\gamma) 
  - NT(\gamma^{1+\tau})x 
  - N_M(\gamma)NT(\gamma^{2+\tau}) .
  \end{split}
\end{equation}
\end{itemize}

Then these definitions help to find a family of quadratic number fields with unramified cyclic quintic extension:
\begin{theorem}
    Let $m$ be a non-negative integer and define $E = split(g_m,\Q)$.Then $E$ is a $D_5$ - extension
of $\Q$ containing $k_m$. Furthermore, if $m \equiv 12 \:(mod\:25$), then $E$ is an unramified cyclic quintic extension of $k_m$. Therefore, putting $m = 25s + 12$, $5$ divides the class number of the quadratic field $\Q(\sqrt{-F_{50s+25}})$.
\end{theorem}
\begin{proof}
Using the result that \begin{equation}
    F_{m+1}= \frac{F_m + L_m}{2}
\end{equation}
it follows that $f_{\delta_m}(x) = g_m(x)$. Also using the fact that $k_m(\zeta)$ is normal over $\Q$, $E\subset k_m(\zeta)$. Now define \begin{equation}
    \mathcal{M}(k)=\{\gamma \in k(\zeta)^{\times}|\gamma^{3+4\tau+2\tau^{2}+\tau^3}\notin k(\zeta)^5\}
\end{equation}
It therefore holds that $\delta_m \in \mathcal{M}(k_m)$ iff $g_m(x)$ is irreducible over $\Q$. Note that both $\{F_n\}$ and $\{L_n\}$ have periods of length 50 modulo 151. For $m\equiv12 \: mod \: 25$ then \begin{equation}
    g_m(x) \equiv x^5 - 10x^3 - 20x^2 + 65x + 28\:(mod \:151)
\end{equation} which is irreducible over $\Q$. Let $\theta$ be a root of this polynomial. By a result by Sase, no primes are totally ramified over $\Q(\theta)$. Therefore $E/k_m$ is an unramified cyclic quintic extension. 
\end{proof}
Kishi gives examples for the class group when $s = 0,1,2,3$. Using Magma, the class group for $s=4$ is calculated:
\begin{example}
Suppose $s=4$, 
\begin{equation}
d = F_{225} = 2 \cdot 5^2 \cdot 17 \cdot 61 \cdot 3001 \cdot 109441 \cdot 230686501 \cdot11981661982050957053616001.
\end{equation} Define $K = \Q(\sqrt{-d})$.
Then $h(K) = 22968615048297879813120$ which is a multiple of 5, and 
\begin{equation}
cl(K) \cong C_2 \times C_2 \times C_2 \times C_2 \times C_4 \times C_{358884610129654372080}.
\end{equation} 
\end{example}
Here is such an example of an imaginary quadratic number field with an unramified cyclic quintic extension:
\begin{example}
Suppose $s=1, m= 37$. Then $F_{75} = 2111485077978050 = 2 \cdot 5^2 \cdot 61 \cdot 3001 \cdot 230686501$. Define $K = \Q(\sqrt{-F_{75}})$, and 

\begin{center}
$g_{37} = x^5 - 10x^3 - 20x^2 + 445836923452397188907628180249985x  - 841994090120605132670921957520010040515272300004
$
\end{center}
with discriminant 

\begin{center}
$2^{24} \cdot 5^{20} \cdot 13^2 \cdot 61^6 \cdot 109^2 \cdot 139^2 \cdot 3001^6 \cdot 464419^2 \cdot 10772623^2 \cdot 230686501^6 \cdot 29020995417137^2 \cdot 460045379989033^2$. 
\end{center}

Using \href{http://magma.maths.usyd.edu.au/calc/}{Magma}, the class group of $K$ was calculated. The factoring was done using SageMath. So $Cl(K) \cong C_{40} $ and $h(K) = 40$ which is divisible by 5. Let $L$ be the splitting field of $g_{37}(x)$. Then $L$ is an unramified $C_5$ - extension of $K$. 
\end{example}


\subsubsection{Smith's Family of Cyclic Quintic Extensions}
Smith \cite{SMITH} also gives a method to find several families of imaginary quadratic number fields with unramified cyclic extensions using Lucas numbers and Fibonacci numbers. \par
 First recall the well-known result that $L_n^2 = 5F_n^2+4(-1)^n$, therefore $\sqrt{5 \cdot L_n^2+20} = 5F_n \in \Z$ for odd $n$. Furthermore for $m,n \in \Z$ , $m|n$ iff $F_m | F_n$. Since $F_5 = 5$, it follows that $5| F_n $ when $n$ is a multiple of 5, and therefore when $n$ is an odd multiple of 5, \\ $\dfrac{L_n^2+4}{125} = \dfrac{F_n^2}{25} \in \Z$. Also for $t = 2L_{20i-15}$ for $i \in \Z$, $\sqrt{\dfrac{t^2+16}{500}} = \dfrac{F_{20i-15}}{5} \in \Z$. \\ \par 

The following three theorems describe infinite families of imaginary quadratic number fields with unramified cyclic quintic extension. For each theorem, an example of field with unramified cyclic quintic extension was calculating using SageMath. 
\begin{theorem}
Suppose $t = 2L_{20i-5}$ for some $i \in \Z$. Define 
\begin{equation}
f_t(x) = x^5 + 10x^3 - 5tx^2-15x-t^2+t-16
\end{equation}
 


with splitting field $L_t$. 
Furthermore define 
\begin{equation}
d_t = -\sqrt{\frac{t^2+16}{500}},\:K_t = \Q(\sqrt{d_t}).
\end{equation}

If $f_t(x)$ is irreducible, $L_t(x)$ defines an unramified $C_5$ - extension of $K_t$. 
\end{theorem}
\begin{example}
Let $i=1$. Then $t=2L_{15} = 2728$,
\begin{equation}
f_t(x) = x^5 + 10x^3 - 13640x^2 - 15x - 7439272,
\end{equation}
\begin{equation}
 K_t = \Q\left(\sqrt{-(2 \cdot 61)}\right)
\end{equation}

 and $disc(f) = 2^{14} \cdot 5^{20} \cdot 11^2 \cdot 61^6$. Then $L_t$ is an unramified $C_5$ - extension of $K_t$. 
\end{example}

\begin{theorem}
Suppose $t = L_{4i-1}$ for some $i \in \Z$. Define 
\begin{equation}
f_t(x) = x^5 -10x^3 - 5x^2t^2+5(t^3+2t^2+4t+5)x-(t^3+2t^2+5t+8),
\end{equation}




   with splitting field $L_t$.  
Furthermore define 
\begin{equation}
d_t = -t(t+2)(\sqrt{5t^2+20}), \: K_t = \Q(\sqrt{d_t}).
\end{equation}



If $f_t(x)$ is irreducible, $L_t(x)$ defines an unramified $C_5$ - extension of $K_t$.
\end{theorem}
\begin{example}
Let $i=2$. Then $t=L_{7} = 29$,
\begin{equation}
f_t(x) = x^5 - 10x^3 - 4205x^2 + 130960x - 760496,
\end{equation}
\begin{equation}
 K_t = \Q\left(\sqrt{-( 5 \cdot 13 \cdot 29 \cdot 31}\right)
\end{equation}

and $disc(f) =2^6 \cdot 5^{10} \cdot 13^6 \cdot 29^2 \cdot 31^6$. Then $L_t$ is an unramified $C_5$ - extension of $K_t$. 
\end{example}
\begin{theorem}
Suppose either $t = L_{20i-15}$ or $t = L_{100i-25}$ for some $i \in \Z$. Define 

\begin{equation}
f_t(x) = (x+4)(x-1)^4 + 20(x-1)^2t + (10x^2-20x+26)t^2 + (5x^2-10x+13)t^3 +(-5x+6)t^4 + 2t^5,
\end{equation}


 with splitting field $L_t$. 
 Furthermore define 

\begin{equation}
d_t = -t(t+2)\left(\sqrt{\frac{t^2+4}{125}}\right), \: K_t = \Q(\sqrt{d_t}).
\end{equation}


  If $f_t(x)$ is irreducible, $L_t(x)$ defines an unramified $C_5$ - extension of $K_t$. 
\end{theorem}

\begin{example}
Let $i=1$. Then $t=L_{5} = 11$, 
\begin{equation}
f_t(x) = x^5 - 10x^3 + 8105x^2 - 89390x + 430621,\:K_t = \Q \left(\sqrt{-( 11 \cdot13)}\right),
\end{equation}


 and $disc(f) =5^{20} \cdot 11^6 \cdot 13^6
$. Then $L_t$ is an unramified $C_5$ - extension of $K_t$. 
\end{example}
For each of these polynomials, $f_t(x)$ is irreducible for all but finitely many values of $t$, giving 3 infinite families of unramified cyclic extensions of imaginary quadratic number fields. 


\subsection{Unramified Extensions of Cyclic Cubic Fields}
Wong \cite{WONG} also gives examples of a cyclic cubic field with an unsolvable unramified extension.
First the following lemma from Galois Theory is useful:

\begin{lemma}
 Let such a field be $L$, and have Galois closure $S$. Then if $K$ is a cyclic cubic field, $SK$ is an $A_5$ - extension of $K$.
\end{lemma}
\begin{proof}
From the Fundamental Theorem of Galois Theory, any $A_5$ - extension cannot contain a $C_3$ - sub-extension. Hence $K \cap S = \Q$ and the result follows.
\end{proof}


The online database of \cite{JONE2} is then used to find a totally real quintic number field ramified at precisely one prime: 


\begin{example}
Let $K$ be the cyclic cubic field by $f(x) = x^3 - x^2 - 3422x + 1521$, with discriminant $disc(f) = 3^2 \cdot 13^2 \cdot 10267^2$, $\Delta(K) = 10367^2$. Also define $L$ to be the splitting field of the quintic polynomial $g(x) = x^5 - 25x^3 - 7x^2 + 116x - 45$. Then $L$ is an $A_5$ - extension of $\Q$, and the compositum $LK$ is an unramified (and unsolvable) $A_5$ - extension of $K$.
\end{example}




\subsection{Yamamura's Results for the First Imaginary Quadratic Field with Unramified Unsolvable extension}


Yamamura \cite{YAMA1997} also proves that $\Q(\sqrt{-1507})$ is the first imaginary quadratic field with an unramified $A_5$ - extension over $\Q$. In fact, defining $L=split\left( x^5-5x^3+5x^2+24x+5,\Q\right)$ gives such an $A_5$ - extension of K. 
\begin{lemma}
Define $K=\Q(\sqrt{-14731})$, $L=split(x^6+3x^5,5x^4+4x^3+3x^2+2x+1,\Q)$. Then $L$ is an unramified $A_6$ - extension of $K$ and is an $S_6$ - extension of $\Q$.
\end{lemma}
\begin{lemma}
Define $K=\Q(\sqrt{-30759})$, $L=split(x^7+2x^6-3x^4-x^3-x^2-x+2,\Q)$. Then $L$ is an unramified PSL(2,7) - extension of $K$ and is an $PSL(2,7)\times C_2$ - extension of $\Q$.
\end{lemma}

\subsection{Hoelscher's Results for Abelian Unramified Extensions}
Using Hoelscher's paper \cite{HOEL} and \cite{JONE}, it is shown that 
the prime $p=239$ is tamely ramified for 
\begin{equation}
  G=S_3, G^{ab} = 2, p_w =3  
\end{equation} and also 
\begin{equation}
    G=D_5,G^{ab} = 2 
\end{equation}
This means that Theorem(1.1) from Hoelscher can be applied \cite{HOEL} with
\begin{equation}
    N = G = D_5, K_0 = \Q
\end{equation}
Then 
\begin{equation}
N/p(N) = D_5 \not\subset \Z/(p-1) = \Z_{238}
\end{equation}
The following diagram shows the field extensions in this situation: 
\begin{center}
    
\begin{tikzpicture}[node distance = 2cm, auto]
      \node (Q) {$\Q$};
      \node (K0) [above of=Q] {$\Q$};
       \node (QZP) [above of=Q, right of=Q] {$\Q(\zeta_{239})$};
       \node (K) [above of=K0] {$D_5$};
       \node (K0ZP) [above of=QZP] {$\Q(\zeta_{239})$};
       \node (KZP) [above of=K0ZP] {$D_5(\zeta_{239})$};
       
       \draw[-] (Q) to node {G/N} (K0);
       \draw[-] (K0) to node {N} (K);
       \draw[-] (K) to node {} (KZP);
       \draw[-] (K0ZP) to node {L} (KZP);
       \draw[-] (QZP) to node {} (K0ZP);
       \draw[-] (Q) to node {} (QZP);
       \draw[-] (K0) to node {} (K0ZP);
      \end{tikzpicture}
\end{center}
\par
Where the field extension $L$ is a non-trivial abelian unramified sub-extension of degree prime to $p$, with $L$ Galois over $\Q$.
Hoelscher also gives the following theorem about the divisibility of the order of Galois groups: 
\begin{theorem}
Let $G$ be the Galois group of some number field, ramified only at 3 and possibly $\infty$. Then \begin{itemize}
\item If $2 \nmid |G|$ and $ 27 \nmid |G|$, then $G$ is cyclic.
\item If $G$ is a solvable quasi-3 group, and $ 27 \nmid |G|$, then $G$ is cyclic.
\end{itemize}
\end{theorem}
The online database at \cite{JONE2} lists 22 number fields ramified only at 3. Note that the converse of this theorem is not true: \cite{JONE2} gives three counterexamples of number fields where $G$ is cyclic, but $2$ divides $|G|$. 
\begin{example}
Let $f(x) = x^2-x+1$. Then $disc(f) = -3$, $G \cong C_2$.
\end{example}
\begin{example}
Let $f(x) = x^6-x^3+1$. Then $disc(f) = -(3^9)$, $G \cong C_6$.
\end{example}
\begin{example}
Let $f(x) = x^{18}-x^9+1$. Then $disc(f) = -(3^{45})$, $G \cong C_{18}$.
\end{example}

\subsection{Lesseni's Results on Degree 9 Number Fields}
Lesseni \cite{LESSENI} proves that there is no primitive number field ramified at only one prime $p<11$. 
Suppose $K=\Q(\theta)$ is a number field where $\theta$ is a root of an irreducible polynomial of degree 9, and let $L$ represent the Galois closure of $K$. $K$ is said to be \textbf{primitive} if it has no cubic subfields. The following theorem is given:
 \begin{theorem}
    Suppose GRH holds. Then $L$ cannot be ramified over $K$ only at $p=5$. Now suppose GRH doesn't hold. Then $5\mathcal{O}_K$ is equal to one of the following: \begin{itemize}
        \item $\mathfrak{p}_1^5\mathfrak{p}_2^4$
        \item $\mathfrak{p}_1^5\mathfrak{p}_2^3\mathfrak{p}_3$
        \item $\mathfrak{p}_1^5\mathfrak{p}_2^2\mathfrak{p}_3^2$
        \item  $\mathfrak{p}_1^5\mathfrak{p}_2^2$
    \end{itemize}
    whence the discriminant $d_K$ is equal to $5^{11}$ or $5^{12}$. 
\end{theorem}
Similar theorems hold for $p=3$ and $p=7$. Using a computer search for primitive number fields defined by a degree 9 polynomial, for a prime $p<11$ there were only 13 distinct number fields found which ramify precisely at $3$, and none of these number fields ramify at $2$,$5$ or $7$. In addition, none of these number fields are primitive, leading to the following conclusion:
\begin{theorem}
    There is no primitive degree 9 number field ramified at only one prime $p$, $p<11$.
\end{theorem}
\begin{corollary}
 Suppose $K$ is a degree 9 number field which is ramified at only one prime p, $p<11$. Then the Galois group of its Galois closure is solvable. 
\end{corollary}
Searching the database of number fields at \cite{JONE2} confirms this result. 



\section{Infinite Unramified Extensions}
\subsection{Imaginary Quadratic Extensions}
Martinet \cite{MART1978} gives the following example of a totally real number field of degree 10 with infinite unramified extension:
\begin{example}
\label{ex:martinet}
Suppose $K = \Q\left(\cos(\frac{2\pi}{11}),\sqrt{2}\right)$. Then $[K:\Q]=10$ and $rd_K = 92.37$. Genus theory and Golod-Shafarevich together show that $K$ has an infinite unramified 2-tower.
\end{example}
 In fact, $K$ has the smallest root discriminant of any known number field with an infinite unramified extension. 
However, if the number field is imaginary quadratic, several examples of infinite unramified extensions have been found. \par
The following is a fact from Algebraic Number Theory: there are 9 imaginary quadratic fields with class number 1, and there are 47 imaginary biquadratic number fields with class number 1. \par One natural question to ask is: "What are the unramified extensions of imaginary quadratic number fields"? Discriminant bounds are one way of attacking this question. Applying Odlyzko's bounds gives this lemma:
\begin{lemma}
All imaginary quadratic number fields with class number one are unramified-closed, and therefore have no infinite unramified extension.  
\end{lemma}
\begin{proof}
Suppose $K$ is a imaginary quadratic number field with class number one. Then $rd_K \leq \sqrt{163} = 12.77 < 17.02 = B(120,0,60)$. So $K$ is unramified-closed by a previous theorem. 
\end{proof}
Such a method does not work for imaginary biquadratic number fields with trivial class group, by considering the field $K=\Q(\sqrt{-67},\sqrt{-163})$ which has root discriminant equal to 104.50. 

\subsection{ Biquadratic Number Fields with Infinite Unramified Extension}
In a paper by Hajir and Maire \cite{HAJIR2002415}, an unpublished paper by Martinet is referenced with the following examples:
\begin{example}
Define $K_1 = \Q\left( \sqrt{-263},{-35}\right)$,$K_1 = \Q\left( \sqrt{-263},{-35}\right)$. Then $K_1$ and $K_2$ have infinite unramified extensions. Furthermore, $rd_{K_1} = 95.94$, $rd_{K_2} = 95.42$.
\end{example}
These biquadratic number fields have root discriminant only slightly larger than the degree 10 number field given by Martinet in \Cref{ex:martinet}. \par

Suppose now that $K$ is a class field with trivial class group, i.e. $h(K)=1$. Then $K$ has no abelian (and hence no
solvable) non-trivial unramified Galois extension. Despite this, $K$ may have a unsolvable unramified extension. Brink \cite{BRINK} gives such an example:
\begin{example}
Suppose
\begin{equation}
   K=\Q(\sqrt{29},\sqrt{4967}) 
\end{equation}
\begin{equation}
   L=split(x^7 - 11x^5 + 17x^3 - 5x + 1,\Q[x])
\end{equation}
Then $K$ has class number 1 and $L$ is a $PSL(2, 7)$ - extension of $K$.
\end{example}

Maire \cite{MAIR} showed that there exist biquadratic number fields with class number one with an infinite unramified extension. Here is another example from Maire: 
\begin{example}
Suppose $K= \Q( \sqrt{17601097}, \sqrt{17380678572159893})$. Then $h(K)=1$ and $K$ has an infinite unramified Galois extension. 
\end{example}

\begin{theorem}
\label{thm:brink}
Brink \cite{BRINK} gives the following construction for 
biquadratic number fields with infinite unramified extension. 
Suppose that \begin{enumerate}
    \item $f\in \Z[x]$ is an irreducible quintic with five real roots.
    \item $D = disc(f)$ is prime and $\Q(\sqrt{L})$ has class number 1.
    \item $p$ and $q$ are two primes such that $\Q(\sqrt{p.q})$ has class number 1 and $\Q\left(\sqrt{(D.p.q}\right)$ has class number 2.
    \item $f(x)$ has five simple roots modulo $p$ and $f(x)$ factors modulo $q$ into polynomials of degrees, as a tuple $\mu$ of the form (1,1,1,1,1),(1,1,1,3),(1,2,2) or (1,1,3).
\end{enumerate}
Then the field $L=\Q\left(\sqrt{D},\sqrt{p \cdot q}\right)$ has class number 1 and infinite unramified extension.
\end{theorem}
\begin{proof}
A result from Kondo \cite{KOND} shows that the splitting field K
of f is an $S_5$ - extension of $\Q$ and an unramified $A_5$ - extension of $\Q(\sqrt{D})$. Hence $M=K\left(\sqrt{p \cdot q}\right)$ is an
unramified $A_5$ - extension of L.In fact, since $M$ has a finite 2-Hilbert tower, the class group of $M$ must be a 2-group. Furthermore, $K$ has class number 1, as demonstrated in the following diagram.
\begin{center}
    \begin{tikzpicture} [align=center]
  \path  (0, 0)   node(Q)  {$\Q$}
          +(6, 1)   node(QD12) {$\Q(\sqrt{D \cdot p \cdot q})$}
          ++(3,1)   node(Q12) {$\Q(\sqrt{p \cdot q)}$}
           ++(-5,0)   node(QD) {$\Q(\sqrt{D})$}
           ++(1,2)   node(K) {$K=split(f,\Q[x])$}
           ++(5,0)   node(L) {$L=\Q(\sqrt{D},\sqrt{p \cdot q})$}
            ++(-1,2)   node(M) {$M=K(\sqrt{p \cdot q})$};
    \draw [-] (Q) to node [pos=0.5,above]{} (Q12);
    \draw [-] (Q) to node [pos=0.8,below]{} (QD);
    \draw [-] (Q) to node [pos=0.5,below]{} (QD12);
  \draw [-] (QD) to node [pos=0.5,left]{$A_5$} (K);
  \draw [-] (Q) to node [pos=0.5,right]{$S_5$} (K);
  \draw [-] (Q) to node [pos=0.5,below]{} (L);
  \draw [-] (Q12) to node [pos=0.5,below]{} (L);
  \draw [-] (QD12) to node [pos=0.5,below]{} (L);
    \draw [-] (L) to node [pos=0.5,right]{$A_5$} (M);
     \draw [-] (K) to node [pos=0.5,above]{$C_2$} (M);
\end{tikzpicture}
\end{center}

Let $r$ be the number of primes $\mathfrak{p}$ in $L$ ramified in $M$, and let $\theta$ be a root of f, $T = \Q(\theta)$. Martinet \cite{MART1978} shows that $M$ has an infinite 2-class field tower if $r\geq 155$. By assumption $p$ splits completely in $T$ and therefore also in $L$; furthermore $q$ decomposes in $T$ as $q = \mathfrak{p}_1...\mathfrak{p}_r$, with inertia degrees
\begin{equation}
    (deg(\mathfrak{p}_1),...deg(\mathfrak{p}_r))=\mu 
\end{equation}
Write $Z_\mathfrak{B}\subseteq\Gamma(L/\Q) = S_5$ as the decomposition group of $\mathfrak{B}$ where $\mathfrak{B}$ is a prime in $L$ dividing $q$. $q$ is unramified, so this group is cyclic, and Martinet \cite{MART1978} shows that $Z_\mathfrak{B}$ has order at most $3$. It now follows that $L$ has $120$ primes dividing $p$ and at least $40$ primes dividing $q$. Then $r\geq 160$ since they all ramify in $M$, and the theorem follows.
\end{proof}

Using SageMath, the following polynomial and primes were found:
\begin{equation}
    f(x)=x^5+4x^4-6x^2-x+1,\:p=1531,\:q=71,151,227,\:disc(f)=170701
\end{equation}
\begin{equation}
 f(x)=x^5-4x^4+12x^2-8x+1,\:p=1987,\:q=31,107,211,239,\:disc(f)=186037
 \end{equation}
These polynomials satisfy the criteria of the \Cref{thm:brink} and therefore describe fields with infinite unramified extensions. Furthermore, the class number of the splitting fields of each of these polynomials is 1, meaning that they are equal to their own Hilbert class fields. \par

\begin{example}
    Using the notation as defined in, \begin{equation}
    f(x)=x^5 - 2x^4 - 20x^3 + 6x^2 + 89x + 67
    \end{equation}
    \begin{equation}
        p=2003,q=499, disc(f)=4906992917
    \end{equation}
    Using Magma, the class group of $K$ is isomorphic to $V_4$. Due to the Fundamental Theorem of Galois Theory, there must exist an intermediate field isomorphic to $C_2$ between $K$ and its Hilbert class field. Furthermore, the Hilbert class field of $K$ is isomorphic to the splitting field of \par
   \begin{polynomial}
   x^{20} - 2874x^{18} + 2391847x^{16} -
    471345876x^{14} + 29106648697x^{12} - 550807754260x^{10} +
    4307861945767x^{8} - 14829016524058x^{6} + 23545104859585x^{4} -
    16530672769260x^{2} + 4009653817744
   \end{polynomial}
\end{example}
\begin{example}
    Using the notation as defined in \Cref{thm:brink}, \begin{equation}
    f(x)=x^5-2x^2-20x^3+6x^2+89x+67
    \end{equation}
    \begin{equation}
        p=811,q=59, disc(f)=8996154317
    \end{equation}
    Using Magma, the class group of $K$ is isomorphic to $C_2$. There is no intermediate field between $K$ and its Hilbert class field. Furthermore, the Hilbert class field of $K$ is isomorphic to the splitting field of \par
   \begin{polynomial}
 x^{10} - 375x^{8} + 5121x^{6} -
    4084x^{4} + 928x^{2} - 64.
   \end{polynomial}
  The splitting field of this polynomial has class group isomorphic to $V_4$.
\end{example}


\subsection{Golod and Shafaverich}
Golod and Shafaverich \cite{GOLO} found a number field with an infinite class tower. This relies on the following theorem:

\begin{theorem}
\label{thm:gs1}
    Let G be a finite p-group, and define $d=dim_{\mathbb{F}_{p}}H^1(G,\mathbb{F}_p)$, $r=dim_{\mathbb{F}_{p}}H^2(G,\mathbb{F}_p)$. 
    Then $r>d^2/4$.
\end{theorem}
There is also the theorem from Shafaverich,1963:

\begin{theorem}
\label{thm:gs2}
    Let $G = \Gamma(H_{K_{\infty}}^{p}/K)$ where $K$ is an imaginary quadratic number field. If $G$ is finitely generated as a pro-p group, then
$r-d\leq 1 $. If $p$ is an odd prime, $r=d$.
\end{theorem}
The inequalities in \Cref{thm:gs1} and \Cref{thm:gs2} give a contradiction for $d \geq 5$ if all such $G$ are assumed to be finite p-groups. Hence there must be a number field with an infinite 2-class field tower, so not all number fields have a finite field extension with class number 1.:
\begin{example}
    Define $K=\Q(\sqrt{-3 \cdot 5\cdot7\cdot11\cdot19\cdot23})$. Then 6 odd primes ramify in $K$ over $\Q$, and so $K$ has an infinite 2-class field tower. 
\end{example}
Furthermore, Schoof \cite{SCHO} shows that $\Q\left(\sqrt{-191\cdot773}\right)$ has an infinite 2-class field tower, and that there are infinitely many real quadratic number fields of the form $\Q(\sqrt{p_1 \cdot p_2})$ possessing infinite class field towers, where $p_1$ and $p_2$ are prime, 

\subsection{Infinite Unramified Extensions of Cyclic Cubic Fields }
Wong also gives a method to find a cyclic cubic field with infinite class field tower and infinite unramified extension. Use the following result from Roquette (see \cite{Koch}):
\begin{theorem}
    Suppose $K$ is a normal degree $n$ number field, r is the number of infinite places over $K$, and $e(p)$ be the nonzero exponent of a prime $p$ in the factorisation of $n$. Let $t_p$ be the number of primes ramified in $K$ with $p$ dividing their ramification index, and $\delta_p$ is 1 if the $p$-th roots of unity are in $K$, and 0 otherwise. Then $K$ has an infinite class tower if \begin{equation}
        t_p\geqslant 2 + e(p)\delta_p + \frac{r-1}{p-1} + 2 \sqrt{r+\delta_p} 
    \end{equation}
 If $K$ is a cyclic cubic field, $n=r=p=3$, $e(p)=1$, $\delta_3 = 0$. Therefore $K$ has an infinite class tower if $t_3 \geq 3 + 2\sqrt{3} = 6.46$. 
\end{theorem}
Hence if $K$ is a cyclic cubic field, with at least $7$ ramified primes, $K$ has an infinite class field tower. Using the algorithm given in the proof of theorem 2.7 in Wong \cite{WONG}, an appropriate polynomial can be calculated. Here is an example:
\begin{example}
    Suppose the discriminant of $K$ is specified to be $(3^4)(7^2)(13^2)(19^2)(31^2)(37^2)(61^2)$. Using SageMath to follow the conditions given by Wong, an appropriate polynomial was found. Set $u = -453459$, $v=1499$. Next define $f(x) = x^3-362918829x + 18285423253279$. Then the cyclic cubic field $K$ defined by $f(x)$ has 7 ramified primes. Therefore $K$ has an infinite class field tower and infinite unramified extension. 
\end{example}




\subsection{Maire's Results for Infinite Unramified Extension}
\subsubsection*{Construction of Quadratic Field with Finite Hilbert Tower and Infinite Unramified Extension}
Maire \cite{MAIR}[3.1], uses a theorem from Kummer Theory is used to find a quadratic field with finite Hilbert Tower and infinite unramified extension:
\begin{theorem}[Kummer Theory]
\label{thm:Kummer}
Suppose $K/\Q$ is a cyclic extension of degree $p$, unramified at $p$, and $L/\Q$ is an extension of degree n. Suppose also that for all places $\mathfrak{Q}$ in $L$, the ramification index of $\Q$ in $L/\Q$ divides the ramification index of $\mathfrak{q} = \Q\cap\mathfrak{Q}$ in $K/\Q$. \par
Then the extension $LK/\Q$ is unramified at all finite places. In particular, $\bar{L}K/K$ is also unramified at all finite places.
\end{theorem}
\subsubsection*{Construction of Suitable Number Field}
Maire gives a construction of such a number field:
\begin{proposition}
\label{prop:maire}
Suppose $K$ is a totally real number field of degree $n$ over $\Q$, and $q_1,q_2$ are distinct prime numbers with the following criteria:
\begin{itemize}

\item $disc(K)$ is equal to some prime $l$.
\item There are precisely $n-2$ unramified places above $l$ in $K/\Q$. 
\item $q_1 \equiv q_2 \equiv 3 $ modulo $4$.
\item $q_1$ splits completely in $K$.
\item There are precisely $n-1$ unramified places above $q_2$ in $K/\Q$. 
\end{itemize}

Also write $k=\Q(\sqrt{l \cdot q_1 \cdot q_2})$ and $M=Kk$. 
Then $k_H/k$ is finite and $k_\infty/k is infinite$.
\end{proposition}


Using \Cref{thm:Kummer}, all places above $q_1$ and $q_2$, as well as the $n-2$ places above $l$ are ramified in $M/K$. Using the theorem from Golod and Shafaverich, for $n \geq 7$, $M$ has some infinite 2-Hilbert tower, denoted by $M_2$. Furthermore, $M/k$ is unramified. This implies that 
$k = \Q(l \cdot q_1 \cdot q_2) \subset M \subset M_2$.\par
$M_2$ is an infinite unramified extension of $k$. But then $\bar{M_2}$ is an infinite unramified Galois extension of $k$. Maire also shows the following:
\begin{theorem}
$k_H/k$ is finite.
\end{theorem}
\begin{proof}
Suppose $k_1$, $k_2$ and $k=k_3$ are quadratic fields with discriminant $l$, $l \cdot q_1$, $l \cdot q_1 \cdot q_2$ respectively, (with $l$, $q_1$, $q_2$ as above), and define $F = k_1 k_2$. Since $l \equiv q_1q_2 \equiv 1$ mod $4$, $F/k_3$ is unramified. In addition, if $h(k_1) = h(k_2) =1$, and $h(k_3) = 2$, then $k_H = F$. Also remark that $h(F)=1$ and that $F/k$ is unramified, so $LF/F$ is an infinite unramified extension.
\end{proof}
\subsubsection*{Examples of Quadratic Fields with Finite Hilbert Tower and Infinite Unramified Extension}
Using SageMath, the following polynomial and primes were found: 
\begin{example}
\begin{equation}
    f(x) = x^7-3x^6-5x^5+17x^4+x^3-14x^2+3x+1, l= disc(f)=8980833629
\end{equation}
Also define $K=split(P,\Q[x])$. Modulo $l$,
\begin{eqnarray*}
        P(x)&=&(x+2040911047)(x+3097257563)\\ & & {} (x+3210721157)(x+6041496066)\\ & & {}(x+6737752038)(x+7397598321)^2
\end{eqnarray*}
Now specify values for $q_1$ and $q_2$:
\begin{equation}
    q_1=17471,q_2\in\{443,919,1627,2803,3691,5231,5867,9391\}
\end{equation}
Then indeed $q_1\equiv\:q_2\equiv3(4)$. Also, $q_1$ splits completely in K, and there are n-1 places lying above $q_2$ in $K/\Q$.
\end{example}
This can be restated as a theorem:
\begin{theorem}
    Suppose $K$ is a quadratic field of the form $\Q(\sqrt{8980833629 \cdot 17471 \cdot q_2})$, where 
    \begin{equation}
        q_2\in\{443,919,1627,2803,3691,5231,5867,9391\}
    \end{equation}
    then \begin{enumerate}
        \item $K_H/K$ is finite.
        \item $K_\infty/K$ is finite.
    \end{enumerate}
\end{theorem}



\subsection{Maire's Results for infinite non Galois unramified extension}
Following from Maire \cite{MAIR}[5.1], there exist infinitely many (imaginary or real) quadratic fields with a finite 2-Hilbert tower, but having an infinite ramified extension of $2^{\infty{}}$. 
The following methodology was implemented in SageMath to find suitable polynomials:
\begin{enumerate}
    \item Pick 8 real numbers close to 0 and define $\tilde{P}(x)$ to be the polynomial with these roots. This is done to increase the probability that P(x) will also have 8 real roots. 
    \item Find a polynomial P(x) which is near to $\tilde{P}(x)$.
    \item Check that the P(x) is irreducible, has 8 real roots and has prime discriminant. 
    \item Search for primes 3 mod 4 which totally decompose in the splitting field of P. 
\end{enumerate}
The following polynomial was found: 
\begin{equation}
    f(x) = x^8 - 3x^7 - 16x^6 + 31x^5 + 74x^4 - 40x^3 - 56x^2 + 17x + 3
\end{equation}
where 
\begin{equation}
    l = disc(f) = 76363470193820546413
\end{equation}
Put \begin{equation}
    q_1 = 219823, q_2 = 931363, K = split(P, \Q[x]).
\end{equation}
\par
Here $q_1$ and $q_2$ are totally decomposed in $K/\Q$, the Galois closure of P.
\par
Use the following definitions: 
\begin{itemize}
    \item $N = K\Q(\sqrt{l})$. Note $q_1$ and $q_2$ decompose completely in $N/\Q$, an extension of degree 16.
    \item $E = N(\sqrt{q_1.q_2})$
    \item $E_2$ is the infinite 2-Hilbert tower of E.
\end{itemize}
\par 
In the following diagram, all extensions are unramified 2-extensions. 

\begin{center}
    \begin{tikzpicture}[node distance = 1cm, auto]
      \node (Q12) {$\Q(\sqrt{l.q_1.q_2})$};
      \node (QL12) [above of=Q12] {$\Q \left(\sqrt{l},\sqrt{q_1 \cdot q_2}\right)$};
      \node (E) [above of=QL12] {E};
      \node (E2) [above of=E] {$E_2$};
      \draw [-] (Q12) to node {} (QL12);
      \draw [-] (QL12) to node {} (E);
      \draw [-] (E) to node {} (E2);
      \end{tikzpicture}
\end{center}
In fact, $E_2/\Q(\sqrt{l \cdot q_1 \cdot q_2})$ is an unramified field extension of degree $2^{\infty}$. Furthermore, the choices of $q_1$ and $q_2$ guarantee that the 2-part of $cl(\Q(\sqrt{q_1 \cdot q_2}))$ will be cyclic, and that the 2-Hilbert tower stops at the first extension. 


\begin{theorem}[Cebotarev's Density Criterion]
Let $L/K$ be a finite extension of
number fields with Galois group $G$, and let $\mathcal{C}$ be a conjugacy class in $G$. Then the set of
prime ideals of $K$ such that $(\mathfrak{p},L/K)=\mathcal{C}$ has density $|\mathcal{C}|/|G|$ in the set of all prime
ideals of $K$. If $G$ is abelian, then, for a fixed $\sigma \in G$, the set of prime ideals $\mathfrak{p}$ of $K$ with $\{\mathfrak{p}:(\mathfrak{p},L/K)=\sigma\}$  = $(G:1)$.
\end{theorem}
\begin{corollary}
\label{cor:ceb}
 If a polynomial $f \in K[x]$ splits into linear factors modulo $\mathfrak{p}$ for all but finitely prime ideals $\mathfrak{p}$ in K, then it splits in $K[x]$.
\end{corollary}
\begin{proof}
Apply the theorem to the splitting field of f.
\end{proof}
Applying \Cref{cor:ceb} to \Cref{prop:maire} proves that there are infinitely many such $q_1$ and $q_2$ satisfying the conditions.
Finally, for an imaginary quadratic number field with the same properties, keep the same $K$ and $q_1$, and put $q_2=-1$, and using $\Q(\sqrt{l \cdot q_1 \cdot q_2})$. 




\section{Maximal Unramified Extensions of Number Fields}
\subsection{P-adics}
For p-adic fields, it is relatively easy to calculate the maximal unramified extension. 
To find $\Q_p^{ur}$, it is necessary to define an unramified extension of a local field $K$. Local Field Theory gives the following results:
\begin{definition}
Suppose $L:K$ is a local field extension. Then $L:K$ is unramified if $[L:K]$ = $[l:k]$, where $l = \co_L\pi_L$ and $ k= \co_K\pi_K$, where $\pi_L,\pi_K$ are the uniformisers of $L,K$. This is equivalent to saying that $\pi_k$ is inert in $L$. 
\end{definition}
\begin{theorem}
\label{thm:res}
Fix a local field $K$ with perfect residue field $k$.. Then there is an equivalence of categories
between the extensions of $k$ and the unramified extensions of $K$. 
\end{theorem}
\begin{example}
Consider the unramified extensions of $\Q_p$. By \Cref{thm:res}, these are in 1-1 correspondence with finite extensions of $\F_p$. For every $n \in \N$, there exists a unique field extension of degree $n$ of $\F_p$, isomorphic to the splitting field of $x^{p^n}-x$. \par Therefore $\Q_p$ has a unique field extension of degree $n$, obtained by adjoining all $\left( p^n-1\right)$-th roots of unity. Furthermore,
$\Q_p^{ur}$ is isomorphic to the algebraic closure of $\F_p$, which is obtained by joining the $\left( p^n-1\right)$-th roots of unity for all $n \in \N$. For any $n$ prime to $p$, $p^{\phi(n)}-1 \equiv 0$ mod $n$, so 
\begin{equation}
\Q_p^{ur} = \Q_p(\left\{ \zeta_n: (n,p)=1 \right\})
\end{equation}
\end{example}
\subsection{Yamamura's First Tables of Quadratic Number Fields with Small Conductor}
%todo check this 
Yamamura \cite{YAMA1997} defines the structure of $\Gamma(K^{ur}/K)$ where $K$ is an imaginary quadratic number field with small conductors. Note that for all number fields with conductor $<1000$, $K_{ur}$ is one of $K_1$, $K_2$ or $K_3$. \par 

Let $K=\Q(\sqrt{d})$ for some integer $d$. Using Odlyzko's bound \Cref{eqn:odlyzko}, the degree $[K^{ur}:K]$ is finite for $|d|\leq 499$, and assuming GRH, replace $499$ with $2003$. It is known that if $[K^{ur}:K_H]<60$, then $K^{ur}=K_H$. However this is difficult to prove; for example for $d=-423$, $K_H=K_1$. It is necessary to find the degree $[K_H:\Q]$. \par 
One way is to use the tower law from Galois theory. Suppose $\Delta(K)=d_1d_2...d_n$, where $\Delta(K)$ is the discriminant of K, then the genus field of $K$ satisfies $K_g=\Q(\sqrt{d_1},\sqrt{d_2},...\sqrt{d_n})$. Therefore there is the list of inclusions \begin{equation}
    \Q \subseteq K \subseteq K_g \subseteq K_1 \subseteq (K_g)_1 \subseteq K_2
\end{equation} and the tower law gives \begin{equation}
    [K_2:q] = [K_2:(K_g)_1]h(K_g)[(K_g)_1:\Q]
\end{equation}\par
Here is an explicit example:
\begin{example}
 Let $d=-1 \cdot 5 \cdot 51=-255\equiv \: 1\:mod\:4$. Therefore $|\Delta(K)|=|d|=255$, and $K_g = \Q(\sqrt{5},\sqrt{51}$. Computer verification gives that $h(K_g)=2$, and so 

\begin{equation}
     [K_2:\Q] = [K_2:(K_g)_1]h(K_g)[(K_g)_1:\Q]= 3*2*4=24
\end{equation}
For $d=-255$, $K_H=K_2$. Then calculating shows that $cl(K)\cong C_6 \times C_2$, 
\begin{equation}
K_1 = K \left( 
\sqrt{5}, \sqrt[3]{(9+\sqrt{85})/2}
\right), K_2 = K_1 \left( 
\sqrt{2+\sqrt{5}(5+2\sqrt{-3})}
\right)
\end{equation}


 In conclusion, Yamamura shows that $\murgg \cong Q_8 \times C_3$.
\end{example}

\subsection{Imaginary Quadratic Number Fields with Class Number Two}
Yamamura \cite{YAMAMURA1996} gives the following result for imaginary quadratic number fields with class number two.
\begin{theorem}
Suppose $K$ is an imaginary quadratic number field with class number 2, i.e. $K=\Q(\sqrt{-d}))$, where $d= 15, 20, 24, 35, 40, 51, 52, 88, 91, 115, 123, 148, 187, 232, 235, 267, 403$, or $427$. Then \begin{itemize}
\item Except for $d = 115, 235, 403$, $K^{ur} = K_1$
\item For $d = 115, 235, 403$, $K^{ur} = K_2$, and $\Gamma(K^{ur}/K)$ can be explicitly calculated. 
\end{itemize}
\end{theorem}
\begin{lemma}
\label{lem:gen}
By genus theory, $d= d_1d_2$, where $d_1$ and $d_2$ are fundamental prime discriminants. Then $K_1 = \Q(\sqrt{d_1},\sqrt{d_2})$. 
\end{lemma}
\begin{proof}
When $d \not \in {115, 235, 403}$, $h(F)=1$ and therefore 
$K_1 =\Q \left(- \sqrt{d_1}, - \sqrt{d_2} \right)$ is an imaginary biquadratic number field with class number one by \Cref{lem:gen}. Since $K_1/K$ is unramified, $rd_{K_1}=rd_K \leq 267=16.340$, and if $d = 427$, and $rd_{K_1}=rd_K = 427=20.663$. Now $B(240, 0, 120) = 18.788$, $(B(240, 0, 120) = 23.575$ under GRH. Hence under GRH, $K_1$ is unramified-closed and $K_{ur}=K_1$ 
\end{proof}
\begin{corollary}
Assume GRH. Define $G = \Gamma\left(\Q(\sqrt{-d})^{ur}/\Q(\sqrt{-d})\right)$. Then there are three situations:
\begin{itemize}
\item If $d \neq 115, 235, 403$, then have $ G \cong C_2$
\item If $d = 115,403$ then $G \cong D_3$.
\item If $d =  235$, $G \cong D_5$. 
\end{itemize}
\end{corollary}

Yamamura also gives the following theorem: 
\begin{theorem}
\label{thm:yam_group}
Suppose $K$ is an imaginary quadratic number field and $G = \Gamma(K^{ur}/K)$. Then unless $G$ is isomorphic to one of $C_2$,$C_3$ or $D_5$, $G^{ab} \not \cong C_2$. 
\end{theorem}
These next two lemmata from Group Theory are useful for finding the abelianisation dihedral groups and symmetric groups:
\begin{lemma}
Suppose $n>5$ is odd. By Group Theory, $D_n^{ab} \cong C_2$. Then $G \not \cong D_n$ for any imaginary quadratic number field.
\end{lemma}
\begin{lemma}
Suppose $n>2$. Then $[S_n] \cong D_n$, meaning that $S_n^{ab} \cong C_2$. By \Cref{thm:yam_group}, $G \not \cong S_n$ for any imaginary quadratic number field.
\end{lemma}
Until the paper by Wong \cite{Wong2015}, GRH was needed to find the maximal unramified extension in the case $d = 427$. Wong removed this dependency. In addition, the following are proved:
\begin{itemize}
\item Unconditionally, the number field $\Q(\sqrt{-7},\sqrt{-61})$ is unramified-closed.
\item Assuming GRH, the degree 14 subfield of the cyclotomic field $\Q(\zeta_{49})$ is also unramified-closed. 
\end{itemize}

\subsection{More Maximal Unramified Extensions of Quadratic Number Fields}
In another paper by Yamamura \cite{YAMA2001}, the table for the $\Q(\sqrt{-d}))^{ur}$ is updated for the missing 19 of the missing 23 values of $d$, apart from $d= -883,-907,-947$. However, if it can be verified that $K^{ur} \neq K_1$ for these fields, then $\Gamma(K^{ur}/K) \cong PSL(2,7) \times cl(K)$. 
A previous paper by Yamamura \cite{YAMA1997} gave the following proposition: 
\begin{proposition}
\label{prop:1507}
For $d=1507 = 11 \cdot 137$, $\Q(\sqrt{-1507})$ is the first imaginary quadratic number field with an unramified $A_5$ - extension which is normal over $\Q$.
Define $f(x) = x^5 -5x^3 + 5x^2 + 24x + 4$, $disc(f) = 581388544 = 2^8 \cdot 11^2 \cdot 137^2$. 
\end{proposition}
Consider now the quadratic number fields defined by 
\begin{equation}
-d = 723, 763, 772, 787, 808, 843, 904, 932, 939, 964, 971, 979
\end{equation}
 which all have Hilbert class tower of length 1. 
\begin{proposition}
For these fields, if $K$ has odd class number, then $K^{ur} = K_1$. 
\end{proposition}
\begin{proof}
 Conditional Odlyzko bounds give that $[K^{ur}:K_1]<168 = |PSL(2,7)|$, and by results on group extensions from Group Theory, it is sufficient to show that $K_1$ does not have a unramified $A_5$ - extension, normal over $\Q$. \par 

 Suppose that $K_1$ had such an extension, denoted by $L$. Then $\Gamma(L/K) \cong \Gamma(K_1/K) \times A_5$, and so $K$ would have an unramified $A_5$ - extension, normal over $\Q$, contradicting \Cref{prop:1507}. Hence $K^{ur} = K_1$. 

\end{proof}
For fields with even class number, for example when

\begin{equation}
-d = 924 = 2^2 \cdot 241, \: h(\Q \left(\sqrt{-924}\right) = |C_2 \times C_6| = 12,
\end{equation}

existing data for quintic polynomials is used. For $K_1$ to have an unramified $A_5$ - extension, normal over $\Q$, it is necessary to find a quintic number field with discriminant $-2^2,241,-2^2 \cdot 241$ or $2^4 \cdot 241$. Such a field does not exist, as can be verified by the online database at \cite{JONE2}. Therefore $K^{ur} = K_1$, and the proof for other number fields with even class number are similar. \par

Yamamura also gives the following example. 
\begin{example}
Suppose $f(x) = x^7 - x^6 - 3x^5 - x^4 + 2x^3 + 4x^2 + 4x + 1$, $E$ is a defined by a root of $f$, and $L = \bar{E}$ is the splitting field of $f$. In addition, define $K=\Q(\sqrt{-3983})$. Noting that $3983 = 7 \cdot 569$, and checking the ramification the rational primes $7$ and $569$ in $E$, it is verified that $KE/K$ is unramified, whence $KL/K$ is also unramified. Therefore $KL$ is an unramified $PSL(2,7)$ - extension of $K$. 
\end{example}

\subsection{Kim and Koenig's Results for Maximal Unramified Extensions}
\subsubsection*{Maximal Unramified Extension for d = 22268}
Kim and Koenig \cite{KIM2017} use Odlyzko's bounds and results from Group Theory to show the following: 
\begin{theorem}
 Define $K=\Q(\sqrt{22268})$, and $22268 = 76\cdot 293$. \\ Also define $L=split(x^6-10x^4-7x^3+15x^2+14x+3,\Q)$. Then $K \subset K_1=\Q(\sqrt{76},\sqrt{293})$, and computer calculation shows that $h(K_1) = 1$, thus $K_1$ has no nontrivial unsolvable extensions. Define $M=LK_1$. Then $M=K^{ur}$, $\Gamma(K^{ur}/K \cong A_5)$, and the extensions are shown in the following diagram:   
\end{theorem}
\begin{center}
    \begin{tikzpicture}[node distance = 1.8cm, auto]
      \node (Q) {$\Q$};
      \node (K) [above of=Q] {K};
      \node (K1) [above of=K] {$K_1$};
      \node (M) [above of=K1] {$M=LK_1$};
      \node (L) [right of=K1] {L};
    \draw [->,out=180,in=180,looseness=1] (Q.west) to node[above][pos=0.6,left]{$A_5\times V_4$}  (M.west);    
    \draw [-] (Q) to node [pos=0.5,left]{$C_2$} (K);
    \draw [-] (K) to node {} (K1);
    \draw [-] (K1) to node {$A_5$} (M);
    \draw [-] (Q) to node [pos=0.6,right]{$A_5$} (L);
    \draw [-] (L) to node [pos=0.1,right,above]{$V_4$} (M);
      \end{tikzpicture}
\end{center}
\subsubsection*{Maximal Unramified Extension for d = -1567}
Kim and Koenig also calculate the maximal unramified extension of an imaginary quadratic number field, where $d = -1567$. 
 Define $K=\Q(\sqrt{-1567})$ and 
\begin{equation}
    L=split(x^9-2x^8+10x^7-25x^6+34x^5-40x^4+52x^3-45x^2+20x-4,\Q)
\end{equation}
The following lemma is a useful result in class field theory and will be applied here:
\begin{lemma}[Abhyankar's Lemma]
    Suppose F is a local field, and $E_1$ and $E_2$ are finite extensions of F with degrees $e_1$ and $e_2$ respectively. In addition, suppose $E_2$ is tamely ramified and $e_2|e_1$. Then $E_1E_2$ is an unramified extension of $E_1$.
 \end{lemma}
Then the following theorem is used:
\begin{theorem}
    Write $G=PSL_2(\mathbb{F}_8)$. Then $L$ is a $G$ - extension of $\Q$ and $1567$ is the only prime in this field which is ramified with index $2$. Abhyankar's Lemma shows that $LK/K$ is unramified at every prime. Since $G$ is a non-abelian simple group, it follows that $L\cap K_1=\Q$. Therefore $\Gamma(LK_1/K_1)\cong \Gamma(L/\Q)\cong G$. Following on from this, $\Gamma(LK_1/\Q \cong G \times D_{15}$. 
\end{theorem}
The field extensions are shown in this diagram:
\begin{center}
    \begin{tikzpicture}[node distance = 2cm, auto]
      \node (Q) {$\Q$};
      \node (K) [above of=Q] {K};
      \node (K1) [above of=K] {$K_1$};
      \node (LK1) [above of=K1] {$LK_1$};
      \node (L) [right of=K1] {L};
    \draw [->,out=180,in=180,looseness=1] (Q.west) to node[above][pos=0.6,left]{$G\times D_{15}$}  (LK1.west);
    \draw [->,out=180,in=180,looseness=1] (Q.west) to node[above][pos=0.6,right]{$D_{15}$}  (K1.west); 
    \draw [-] (Q) to node [pos=0.4,left]{$C_2$} (K);
    \draw [-] (Q) to node [pos=0.6,right]{G} (L);
    \draw [-] (K) to node {} (K1);
    \draw [-] (K1) to node {G} (LK1);
    \draw [-] (L) to node [pos=0.5,right]{$D_{15}$} (LK1);
      \end{tikzpicture}
\end{center}
\subsection{Real Quadratic Number Fields with Unsolvable Maximal Unramified Extension}
In this section, GRH is assumed. Under this assumption, Kim \cite{KIM2016235} shows that for $d \in \{13613,16621,16701\}$, $\Gamma(\Q(\sqrt{d})^{ur}/\Q(\sqrt{d}))$ is isomorphic to an unsolvable finite group.
\subsubsection*{Definitions}
The following definitions are from Group Theory
\begin{definition}
Suppose $G$ is a group. The \textbf{automorphism group} $Aut(G)$ is the group consisting of all the automorphisms of $G$. 

\end{definition}

\begin{definition}
Suppose $N$ and $Q$ are two groups. $G$ is an \textbf{extension} of $Q$ by $N$ if there exists a short exact sequence 
\begin{equation}
1 \rightarrow N \rightarrow G \rightarrow Q \rightarrow 1 
\end{equation}
Such an extension is called a \textbf{central extension} if the centre of $G$ contains $N$. 
\end{definition}
\begin{definition}
A \textbf{p-group} for a given prime number p is a group in which every element has order a power of p.
\end{definition}
The following proposition from Group Theory is relevant:
\begin{proposition}
\label{prop:group_hardcore}
Let $H$ be an abelian 2-group. Suppose that $1 \rightarrow H \rightarrow G \rightarrow A_5 \rightarrow 1$ is a central extension of $A_5$ by $H$. If $|H| > 2$ then $G$ has a non-trivial abelian quotient, whereas if $|H|=2$, then G is isomorphic either to $C_2 \times A_5$ or to $SL_2(F_5)$.
\end{proposition}

 \subsubsection*{Calculation of the Maximal Unramified Extension of Certain Fields}
 Kim also gives several examples for the determination of the maximal unramified extension of certain quadratic number fields: 
Let $K= \Q(\sqrt{13613})$, $L$ be the splitting field of $f(x)=x^6-13x^4-7x^3 +44x^2 +40x-9$, and $E$ be a number field defined by a root of $f$, so $L$ is the Galois closure of $E$. Then $f$ has a discriminant of $163^2$ and factorises as
\begin{equation}
(x+4519)(x+6371)^2(x+10315)(x+13438)^2 \: mod \: 13613.
\end{equation}
Therefore $L$ is an $A_5$ - extension of $\Q$ unramified only at 13613 with ramification index 2. By Abhyankar's Lemma, $LK/K$ is unramified at all primes. $A_5$ is an non-abelian simple group, so $L \cap $K$ = \Q$ and $\Gamma(LK/K) \cong \Gamma(L/\Q) \cong A_5$, whence $LK$ is an unramified $A_5$ - extension of $K$. \par
Now write $M=LK$. Since $M/K$ is unramified at all places, $M$ and $K$ have the same root discriminant, $rd_M = rd_K = \sqrt{13613} = 116.67 < 121.11 = B(2400,2400,0)$. Therefore $[K^{ur}:M]<20$. \\ \par
Now define $N=KE$, and $N$ is a subfield of $M$, so $N/K$ is unramified. Following the known fact that $N/M \cong D_5$, the Fundamental Theorem of Galois Theory shows that there must exist some intermediate field $F$, $M/F/N$ with $\Gamma(M/F) \cong A_5$ and $\Gamma(F/N) \cong C_2$. \par
 Calculation gives that $h(N)=4$ and $cl(N) \cong C_4$, whence $M$ has some unramified $C_2$ - extension $T$ with closure $S = \bar{T}$. Therefore $S/M$ is an unramified extension with Galois group $\Gamma(S/M) \cong \left(C_2 \right)^{n}$ for some $1 \leq n \leq 4$. \\ \par
For $n=2$, $|Aut((C_2)^2)| = |C_2| = 2$, and for $n=3$, $|Aut((C_2)^3)| = |PSL(3,2)| = 168$. In either case, the order is not divisible by 60, so $\Gamma(M/K)$ acts trivially on $\Gamma(S/M)$. By \cref{prop:group_hardcore}, $\Gamma(S/K)$ has an abelian quotient, contradicting $h(K)=1$.\\ \par

Now suppose that $n=4$. 
If $\Gamma(M/K)$ acts trivially on $\Gamma(S/M)$, applying \Cref{prop:group_hardcore} will lead to a contradiction. Let $\tilde{N}$ denote the unique intermediate field in $N_2/\tilde{N}/N$, and $\Gamma(N_2/\tilde{N})$ is an abelian quotient of $\Gamma(S/\tilde{N})$. \\ 
Noting that $\Gamma(S/\tilde{N})$ is a $C_5$ - extension of
$\Gamma(M/\tilde{N})$ by $\Gamma(S/M) \cong (C_2)^{4}$. Since 
$\Gamma(M/\tilde{N})$ acts non-trivially on $\Gamma(S/M)$
 and it follows that $\Gamma(S/\tilde{N})$ does not have $C_2$ as a quotient, with contradiction. \\ \par
Therefore, $m = 1$, implying that $S=T$ and $\Gamma(T/M) = \Gamma(S/M) \cong C_2$. By the \cref{prop:group_hardcore}, $\Gamma(T/K) \cong A_5 \times C_2$ or $\cong SL_2(\mathbb{F}_5)$ However, $A_5 \times C_2$ has an abelian quotient. Therefore, $SL_2(F_5)$ is the only possibility. Since $T$ is a $\Q$ - extension of degree 240, $[K^{ur}:T] < 10$. 

\subsubsection{p-class Groups of T}

Let $T^p$ be the Hilbert p-class field of T. Since T is Galois over $\Q$, so is $T^p$.
\begin{lemma}
There does not exist a group $G$ with $|G| < 10 $ such that $Aut(G)$ contains a subgroup isomorphic to $A_5$ or $SL_2(\mathbb{F}_5)$
\end{lemma}
\begin{proof}
Easy check. 
\end{proof}
\begin{corollary}
\label{cor:trivially}
 $\Gamma(T/K) \cong (SL_2(\mathbb{F}_5))$ acts trivially on $\Gamma(T^p/K)$. Therefore 
$\Gamma(T^p/K)$ is a central extension of $SL_2(\mathbb{F}_5)$ by $\Gamma(T^p/T)$. \par
Since $\Gamma(T/M) \cong C_2$, $\Gamma(T^p/M)$ is abelian and $\Gamma(T^p/K)$ is a central extension of $\Gamma(M/K) \cong A_5$ by some abelian group $\Gamma(T^p/M)$.
\end{corollary}
 By \Cref{prop:group_hardcore} and \Cref{cor:trivially}, $\Gamma(T^p/K)$ has an abelian quotient, contradicting $h(K)=1$. \par
Therefore $\Gamma(K^{ur}/T)$ is trivial and so $\Gamma(K^{ur}/K) \cong SL_2(\mathbb{F}_5)$. Note that $SL_2(\mathbb{F}_5)$ is an unsolvable group. 
 \par
Here are two more examples of the maximal unramified extension of quadratic number fields from Kim:
\begin{example}
Suppose $K = \Q(\sqrt{16621})$ and $f(x) = x^6-13x^4-4x^3 +36x^2 +3x-22$. Then $disc(f) = 11^2 \cdot 1511^2 = 16621^2$. Let $L$ be the splitting field of $f$, and so $L$ is an unramified $A_5$ - extension of $K$ and similar to the previous example, $\Gamma(K^{ur}/K) \cong SL_2(\mathbb{F}_5)$.
\end{example}
\begin{example}
Let $K$ be the real quadratic field $\Q(\sqrt{16701})$. Then, under the assumption of GRH, $\Gamma(K^{ur}/K) \cong A_5 \times C_2$. Since $A_5$ is a subgroup of $A_5 \times C_2$, and $A_5$ is not solvable, $A_5 \times C_2$ is also not solvable.
\end{example}
 


\subsection{Serre's Calculation of Maximal Unramified Extensions of Quadratic number Fields}
\subsubsection*{Maximal Unramified Extension for d = -23}
Serre \cite{SERR} gives two examples of the maximal unramified extension of a quadratic number field:
Consider the polynomial \begin{equation}
 f(x)=x^3-x-1,\: disc(f)=-23
\end{equation}
Note f has one real root and two imaginary roots. Let $L$ denote its splitting field. Then $\Gamma(L/\Q)\cong S_3$ and it is a degree three extension of the quadratic field $K= \Q(\sqrt{-23})$. Now $h(K)=3$ so using Odlyzko's bounds proves that $L$ is the maximal unramified abelian extension of $K$, and Martinet shows that indeed $L = K^{ur}$. The relationships between fields are shown in the diagram below:
\begin{center}
    \begin{tikzpicture}[node distance = 1.8cm, auto]
      \node (Q) {$\Q$};
      \node (K) [above of=Q] {K};
      \node (L) [above of=K] {$L=K^{ur}$};
    \draw [->,out=180,in=180,looseness=1] (Q.west) to node[above][pos=0.6,left]{$S_3$} (L.west);    
    \draw [-] (Q) to node [pos=0.5,right]{$C_2$} (K);
        \draw [-] (K) to node [pos=0.1,left]{} (L);
      \end{tikzpicture}
\end{center}
\subsection{Maximal Unramified Extension for d = -283}
Note that this result is also tabulated in Yamamura's paper \cite{YAMA1997}. 
Define \begin{equation}
    f(x)=x^4-x-1, \: disc(f)=-283
\end{equation}
First observe that $f$ has two real and two imaginary roots. Define $L = split(f,\Q)$ and note that $\Gamma(L/\Q)\cong S_4$. By the Fundamental Theorem of Galois Theory, there exists an intermediate field $H$ corresponding to the normal subgroup $V_4$ of $S_4$. Now $L^H$ is the Hilbert class field of $K= \Q(\sqrt{-283})$ and $h(K)=3$. 
\par
Now define a further field extension of $M/L$ such that $M$ is unramified over $L$ (and hence also over $K$) and $M$ is a Galois extension of $\Q$. A construction (given by Tate) is that $M = L(\sqrt{4-7 \theta^2})$, where $\theta$ is a root of $f$in $L$. \par 
 
Martinet proved that $M$ is the maximal unramified extension of $K$, and $\Gamma(M/K) \cong SL_2(\mathbb{F}_3)$, of order 24. In addition, the Galois group of $M/\Q$ is isomorphic to $GL_2(\mathbb{F}_3)$. The relationships between fields are shown in the diagram below:
\begin{center}
    \begin{tikzpicture} [align=center]
  \path  (0, 0)   node(Q)  {$\Q$}
          +(4, 1)   node(H) {H}
          +(4,3)   node(L) {L}
          ++(0,6)   node(M) {M}
            +(-4,-3)   node(K) {K};
    \draw [-] (Q) to node [pos=0.5,below]{$A_3$} (H);
    \draw [-] (H) to node [pos=0.5,below]{} (L);
    \draw [-] (Q) to node [pos=0.5,below]{$C_2$} (K);
    \draw [-] (L) to node [pos=0.5,below]{} (M);
    \draw [-] (Q) to node [pos=0.5,below]{$S_4$} (L);
    \draw [-] (Q) to node [pos=0.5,right]{$GL_2(F_3)$} (M);
    \draw [-] (K) to node [pos=0.5,left]{$SL_2(F_3)$} (M);

\end{tikzpicture}
\end{center}


\subsection{Maximal Unramified Extensions of Cyclic Cubic Fields}
The maximal unramified extensions of quadratic number fields have been well-studied, and some examples have been given in this section already. In the paper by Wong \cite{WONG}, examples of maximal unramified extensions of cyclic cubic number fields are given.\par

Let $K=\Q(\theta)$ where $\theta$ is the root of a cubic polynomial $f(x)$. If $\Gamma(K/\Q) \cong A_3$, call $K$ a \textbf{cyclic cubic field}.
\begin{proposition}[Galois Theory]
Then $K$ is a cyclic cubic field iff disc(f) is a square. 

\end{proposition} If $K$ is a totally real cubic number field, the unconditional bound for the root discriminant given by Odlyzko (and published by Martinet) is $46.42$. Assuming GRH can increase this value to $72.55$. Wong \cite{WONG} tabulates the all cyclic cubic fields ramified at one prime with trivial class group. 
\begin{theorem}
The first 28 (47 under GRH) cyclic cubic fields with class number 1 have trivial maximal unramified extension.
\end{theorem}
\begin{example}
    Let $f=x^3-x^2-2x+1$. Then $\Delta(K)=7^2$, $rd_{k}=3.66$ and h(K)=1. Then unconditionally, $K$ does not have an unsolvable unramified extension and $\Gamma(K/\Q)\cong C_3$.
\end{example}
\begin{example}
    $f(x)=x^3 -x^2 -110x +49$, $\Delta(K)=331^2$, $72.55 > rd_{K}=47.85 > 46.42$. Therefore under the assumption of GRH, $K$ does not have an unsolvable unramified extension, $\Gamma(K/\Q)\cong C_3$, but without this assumption, Odlyzko's bound is not strong enough to conclude this.
\end{example}


Wong also gives examples of how to calculate the maximal unramified extension of a cyclic cubic field with nontrivial class group. \begin{example}
    $f=x^3-x^2-54x+169$, disc(K)=$163^2$, $rd_{k}=29.84$. Here 
     the class number $h(K)=4$. Define $g(x)=x^6-3x^5-11x^4+27x^3-3x^2-11x+1$. Then the online database at \cite{JONE2} gives $L = split(g,\Q)$ with $\Delta(K_1)=163^4$. \par

     Firstly $\Gamma(L/\Q) \cong A_4$, and 163 is unramified in $L/K$. Hence indeed $L=K_1$. It is known that $\Gamma(L/K)\cong V_4$ which is a normal subgroup of $A_4$. Now h(L)=1 and $rd_K < 54.62$ which is the lower bound for the root discriminant of totally real fields of degree 720, certainly $\Gamma(K^{ur}/K) \cong V_4$ and $\Gamma(K^{ur}/\Q) \cong A_4$. 
\end{example}
\begin{example}
K is the cyclic cubic field defined by $x^3-x^2-104x-371$ with $d_K = 313^2$
and $rd_{K} = 46.10$. Now h(K)=7. Define $g(x) = x^7-x^6-15x^5+20x^4+33x^3-22x^2-32x+8$. \par
Calculation shows that $K_1=split(g,\Q)$ with field discriminant $313^4$. Since $h(K_1) = 1$ and $rd_K = 46.10 < 56.47$ Since $56.47$ is the lower
bound for totally real fields of degree $1260$, indeed $K^{ur}=K_1$ In this
case, $\Gamma(K^{ur}/K) \cong C_7$ and $\Gamma(K^{ur}/\Q) \cong F_{21} $.  
\end{example}
%todo write examples and last yamamura paper
%todo Assume the generalized Riemann hypothesis for the zeta functions of number fields explain GRH

\bibliographystyle{plain}
% \bibliographystyle{unsrtnat}
\bibliography{my_bibliography.bib}
\end{document}
